%!TEX TS-program = xelatex
%!TEX encoding = UTF-8 Unicode

\documentclass[11pt, a4paper]{article}

% For overview tables...
\usepackage{booktabs}
\usepackage{caption}
\usepackage{float}

% LAYOUT
%--------------------------------
% Margins
\usepackage{geometry} 
\geometry{a4paper, left=35mm, right=35mm, top=25mm, bottom=25mm}

% Do not indent paragraphs
\setlength\parindent{0in}

% Enable multicolumns
\usepackage{multicol}
\setlength{\columnsep}{-3.5cm}

% Reduce spacing between bullet points
\usepackage{enumitem}

% Uncomment to suppress page numbers
% \pagenumbering{gobble}

% LANGUAGE
%--------------------------------
% Set the main language
\usepackage{polyglossia}
\setmainlanguage{en-GB}

% TYPOGRAPHY
%--------------------------------
\usepackage{fontspec} 
\usepackage{xunicode}
\usepackage{xltxtra}
% converts LaTeX specials (quotes, dashes etc.) to Unicode
\defaultfontfeatures{Mapping=tex-text}
\setromanfont [Ligatures={Common}, Numbers={OldStyle}]{Minion Pro}
% Cool ampersand
\newcommand{\amper}{{\fontspec[Scale=.95]{Minion
Pro}\selectfont\itshape\&}}

% MARGIN NOTES
%--------------------------------
\usepackage{marginnote}
\newcommand{\note}[1]{\marginnote{\scriptsize #1}}
\renewcommand*{\raggedleftmarginnote}{}
\setlength{\marginparsep}{7pt}
\reversemarginpar

% HEADINGS
%--------------------------------
\usepackage{sectsty} 
\usepackage[normalem]{ulem} 
\sectionfont{\rmfamily\mdseries\bfseries\scshape} 
\subsectionfont{\rmfamily\mdseries\bfseries\scshape\normalsize} 
\subsubsectionfont{\rmfamily\upshape\normalsize} 

% PDF SETUP
%--------------------------------
\usepackage{hyperref}
\hypersetup
{
  pdfauthor={Dr.~John McLevey \newline \footnotesize he/him},
  pdfsubject={Dr.~John McLevey \newline \footnotesize he/him's CV},
  pdftitle={Dr.~John McLevey \newline \footnotesize he/him's CV},
  colorlinks, breaklinks, xetex, bookmarks,
  filecolor=black,
  urlcolor=[rgb]{0.117,0.682,0.858},
  linkcolor=[rgb]{0.117,0.682,0.858},
  linkcolor=[rgb]{0.117,0.682,0.858},
  citecolor=[rgb]{0.117,0.682,0.858}
}

% DOCUMENT
%--------------------------------
\begin{document}

{\LARGE Dr.~John McLevey \newline \footnotesize he/him}\\[.05cm]

\begin{multicols}{2}

Knowledge Integration (KI)\\
Sociology \& Legal Studies (SLS)\\
University of Waterloo\\
Waterloo, ON, Canada\\
Citizenship: Canadian\\

\vspace{-10pt}

+1 (647) 921-2044\\
\href{mailto:john.mclevey@uwaterloo.ca}{john.mclevey@uwaterloo.ca}\\

\columnbreak

\href{http://www.johnmclevey.com/}{www.johnmclevey.com/}\\
\href{http://github.com/mclevey/}{github.com/mclevey/}\\
\end{multicols}

\section*{Appointments}
\noindent
\note{2022--Present}\textbf{\textsc{Associate Chair (Undergraduate)}}\\
{\emph{Vanessa Schweizer was ACUG during my 6-month sabbatical (2023)
and parental leave (2024)}}\\
{Knowledge Integration, Faculty of Environment}\\
{\vspace{-\baselineskip}}\\
{University of Waterloo}
\\[.2cm]
\note{2019--Present}\textbf{\textsc{Associate Professor (with
tenure)}}\\
{\emph{ADDS Status - Approved Doctoral Dissertation Supervisor}}\\
{Knowledge Integration, Faculty of Environment}\\
{Sociology \& Legal Studies, Faculty of Arts}\\
{University of Waterloo}
\\[.2cm]
\note{2013--2019}\textbf{\textsc{Assistant Professor (tenure track)}}\\
{\emph{ADDS Status - Approved Doctoral Dissertation Supervisor}}\\
{Knowledge Integration, Faculty of Environment}\\
{Sociology \& Legal Studies, Faculty of Arts}\\
{University of Waterloo}
\\[.2cm]

\section*{Affiliations}
\noindent
\note{2023}\textbf{\textsc{Visiting Scholar}}\\
Department of Sociology, University of British Columbia\\
Vancouver, BC, Canada
\\[.2cm]
\note{2019}\textbf{\textsc{Visiting Scholar}}\\
Political and Social Sciences, Scuola Normale Superiore\\
Florence, Tuscany, Italy
\\[.2cm]
\note{2014--Present}\textbf{\textsc{WICI Affiliate Researcher}}\\
Waterloo Institute for Complexity and Innovation (WICI), University of
Waterloo\\
Waterloo, ON, Canada
\\[.2cm]
\note{2014--Present}\textbf{\textsc{Policy Fellow}}\\
Balsillie School of International Affairs (BSIA)\\
Waterloo, ON, Canada
\\[.2cm]
\note{2018--Present}\textbf{\textsc{Co-Organizer and Instructor for
Science Outside the Lab, North}}\\
Forum on Science, Policy, and Society\\
Ottawa, Montréal, Vancouver, and Victoria (Canada)
\\[.2cm]
\note{2019--2020}\textbf{\textsc{Leadership Team Member}}\\
Knowledge Development and Exchange Hub: Child and Youth Mental Health
Promotion\\
Funded by the Public Health Agency of Canada
\\[.2cm]
\note{2014--2017}\textbf{\textsc{Board Member}}\\
University of Waterloo Survey Research Centre\\
Waterloo, ON, Canada
\\[.2cm]

\vspace{-24pt}
\section*{Education}
\noindent
\note{2013}\textbf{PhD, Sociology}\\
\emph{McMaster University}, Hamilton, ON, Canada
\\[.2cm]
\note{2009}\textbf{MA, Sociology}\\
\emph{McMaster University}, Hamilton, ON, Canada
\\[.2cm]
\note{2008}\textbf{BA(H), Sociology \& Political Science}\\
\emph{Memorial University}, St.~John's, NL, Canada
\\[.2cm]

\vspace{-24pt}
\section*{Research Areas}
Computational Social Science, Networks, Cognitive Social Science, Public
Opinion, Political Sociology, Sociology of Science and Technology,
Environmental Politics, Quantitative Methodology and Scientific
Computing, Generative Modelling, Bayesian Statistics, Natural Language
Processing and Text Analysis

\vspace{-12pt}
\section*{Publications}

\begin{table}[H]
\raggedleft
\caption*{\raggedleft \emph{Overview of Publications Since 2013}}
\input{templates_and_tables/publications.tex}
\end{table}

\subsection*{Books}
\noindent
  \note{2023}John McLevey, John Scott, and Peter J. Carrington
(Eds). \emph{The Sage Handbook of Social Network Analysis, Volume
2}. London, UK: Sage. 
  \\[.2cm]
  \note{2022}John McLevey. \emph{Doing Computational Social
Science}. London, UK: Sage. 
  \\[.2cm]
  \note{2022}Harry Collins, Rob Evans, Martin Innes, Will Mason-Wilkes,
Eric Kennedy, and John McLevey. \emph{The Face to Face Principle and the
Internet: Science, Trust, Truth and Democracy}. Cardiff, UK: Cardfiff
University Press. 
  \\[.2cm]
  \note{2020}Mark Stoddart, Alice Mattoni, and John
McLevey. \emph{Industrial Development and Eco-Tourisms: Is Co-existence
Possible Between Oil Exploration and Nature Conservation?}. London,
UK: Palgrave MacMillan. 
  \\[.2cm]

\subsection*{Journal Articles}
(Student co-authors are \emph{italicized})\\

\noindent
  \note{2023}David Tindall, Nina Kolleck, and John McLevey. ``Social
Networks and Anthropogenic Climate Change (Special Issue
Introduction).'' \emph{Social Networks}.  
  \\[.2cm]
  \note{2022}\emph{Alexander Graham}, John McLevey, \emph{Tyler Crick},
and \emph{Pierson Browne}. ``Structural Diversity is a Poor Proxy for
Information Diversity: Evidence from 25 Scientific
Fields.'' \emph{Social Networks}. 70: 55-63. 
  \\[.2cm]
  \note{2022}John McLevey, \emph{Tyler Crick}, \emph{Pierson Browne},
and Darrin Durant. ``A New Method for Computational Cultural
Cartography: From Neural Word Embeddings to Transformers and Bayesian
Mixture Models.'' \emph{Canadian Review of Sociology / Revue canadienne
de sociologie}. 59(2): 228-250. 
  \\[.2cm]
  \note{2022}David Tindall, John McLevey, \emph{Yasmin Koop-Monteiro},
and \emph{Alexander Graham}. ``Big Data, Computational Social Science,
and Other Recent Innovations in Social Network
Analysis.'' \emph{Canadian Review of Sociology / Revue canadienne de
sociologie}. 59(2): 271-288. 
  \\[.2cm]
  \note{2022}Allyson Stokes, Janice Aurini, Jessica Rizk, Rob Gorbet,
and John McLevey. ``Using Robotics to Support the Acquisition of
21\textsuperscript{st} Century Competencies: Promising (and Practical)
Directions.'' \emph{Canadian Journal of Education / Revue Canadienne De
l'éducation}. 45(4): 1141--1170. 
  \\[.2cm]
  \note{2022}Jessica Rizk, Janice Aurini, Allyson Stokes, Rob Gorbet,
and John McLevey. ``Leading through the COVID-19 Pandemic: Research with
Canadian Education Leaders.'' \emph{Canadian Journal of Educational
Administration and Policy}.  
  \\[.2cm]
  \note{2021}Igor Grossman, Oliver Twardus, Michael E. W. Varnum, Eranda
Jayawickreme, and John McLevey. ``Expert Predictions of Societal Change:
Insights from the World after COVID Project.'' \emph{American
Psychologist}. 77(2): 276--290. 
  \\[.2cm]
  \note{2021}Kathryn S. Plaisance, \emph{Janet Michaud}, and John
McLevey. ``Pathways of Influence: Understanding the Impacts of
Philosophy of Science in Scientific
Domains.'' \emph{Synthese}. 199: 4865--4896. 
  \\[.2cm]
  \note{2020}Mark Stoddart, John McLevey, Vanessa Schweizer, and
Catherine Wong. ``Climate Change and Energy Futures: Theoretical
Frameworks, Epistemological Issues, and Methodological
Perspectives.'' \emph{Society \& Natural Resources}. 33(11): 1331-1338. 
  \\[.2cm]
  \note{2019}Kathryn S. Plaisance, \emph{Alexander V. Graham}, John
McLevey, and \emph{Janet Michaud}. ``Show Me the Numbers: A Quantitative
Portrait of the Attitudes, Experiences, and Values of Philosophers of
Science.'' \emph{Synthese}. 198: 4603-4633. 
  \\[.2cm]
  \note{2018}Owen Gallupe, John McLevey, and Sarah Brown. ``Selection or
Influence? A Meta-Analysis of the Association between Peer and Personal
Offending.'' \emph{Journal of Quantitative Criminology}. 35: 313-335. 
  \\[.2cm]
  \note{2018}John McLevey, \emph{Alexander Graham}, \emph{Reid
McIlroy-Young}, \emph{Pierson Browne}, and Kathryn S.
Plaisance. ``Interdisciplinarity and Insularity in the Diffusion of
Knowledge: An Analysis of Disciplinary Boundaries Between Philosophy of
Science and the Sciences.'' \emph{Scientometrics}. 117(1): 331-349. 
  \\[.2cm]
  \note{2017}John McLevey and \emph{Reid McIlroy-Young}. ``Introducing
\emph{metaknowledge}: Software for Computational Research in Information
Science, Network Analysis, and Science of Science.'' \emph{The Journal
of Informetrics}. 11: 176-197. 
  \\[.2cm]
  \note{2016}Allyson Stokes and John McLevey. ``From Porter to Bourdieu:
The Evolving Specialty Structure of English Canadian Sociology, 1966-
2014.'' \emph{Canadian Review of Sociology / Revue canadienne de
sociologie}. 53(2): 176-202. 
  \\[.2cm]
  \note{2015}John McLevey. ``Understanding Policy Research in Liminal
Spaces: Think Tank Responses to Diverging Principles of
Legitimacy.'' \emph{Social Studies of Science}. 45(2): 270-293. 
  \\[.2cm]
  \note{2014}John McLevey. ``Think Tanks, Funding, and the Politics of
Policy Knowledge in Canada.'' \emph{Canadian Review of Sociology / Revue
canadienne de sociologie}. 51(1): 54-75. 
  \\[.2cm]

\subsection*{Chapters in Edited Volumes}
(Student co-authors are \emph{italicized})\\

\noindent
  \note{2023}\emph{Pierson Browne}, \emph{Tyler Crick}, and John
McLevey. ``Inferential Network Clustering with Hierarchical Bayesian
Stochastic Blockmodels.'' In John McLevey, John Scott, and Peter J.
Carrington (Eds). \emph{The Sage Handbook of Social Network Analysis,
Volume 2}. London, UK: Sage. \\[.2cm]
  \note{2023}\emph{Pierson Browne}, \emph{Adam Howe}, \emph{Yasmin
Koop-Monteiro}, \emph{Yixi Yang}, and John McLevey. ``Scientific
Software for Network Analysis.'' In John McLevey, John Scott, and Peter
J. Carrington (Eds). \emph{The Sage Handbook of Social Network Analysis,
Volume 2}. London, UK: Sage. \\[.2cm]
  \note{2023}John Scott, John McLevey, and Peter J.
Carrington. ``Introduction.'' In John McLevey, John Scott, and Peter J.
Carrington (Eds). \emph{The Sage Handbook of Social Network Analysis,
Volume 2}. London, UK: Sage. \\[.2cm]
  \note{2023}John McLevey, Allyson Stokes, and \emph{Amelia
Howard}. ``L'influence inégale de Bourdieu sur la sociologie canadienne
anglophone (French translation of `Pierre Bourdieu's Uneven Influence on
Anglophone Canadian Sociology').'' In Amín Pérez and Franck
Poupeau (Eds). \emph{Bourdieu dans les Amériques. Genèses et usage d'une
internationale scientifique}. Aubervilliers, France: l'IHEAL. \\[.2cm]
  \note{2021}John McLevey and Tyler Crick. ``Machine Learning and Neural
Network Language Modelling for Sentiment Analysis.'' In Luke Sloan and
Anabel Quan-Haase (Eds). \emph{The Sage Handbook of Social Media
Research}. London, UK: Sage. \\[.2cm]
  \note{2021}John McLevey, Pierson Browne, and Tyler
Crick. ``Reproducibility, Transparency, and Principled Data
Processing.'' In Uwe Engel and Anabel Quan-Haase (Eds). \emph{Handbook
of Computational Social Science}. New York, US: Routledge. \\[.2cm]
  \note{2021}David Tindall, Mark Stoddart, John McLevey, Lorien Jasny,
Dana R. Fisher, Jennifer Earl, and Mario Diani. ``The Challenges and
Opportunities of Ego-Network Analysis of Social Movements and Collective
Action.'' In Mario Small, Brea Perry, Bernice Pescosolido, and Edward
Smith (Eds). \emph{Personal Networks: Classic Readings and New
Directions in Ego-centric Analysis}. Cambridge: Cambridge University
Press. \\[.2cm]
  \note{2018}John McLevey, Allyson Stokes, and \emph{Amelia
Howard}. ``Pierre Bourdieu's Uneven Influence on Anglophone Canadian
Sociology.'' In Thomas Medvetz and Jeff Sallaz (Eds). \emph{The Oxford
Handbook of Pierre Bourdieu}. Oxford: Oxford University Press. \\[.2cm]
  \note{2018}John McLevey and \emph{Ryan Deschamps}. ``The Sociology of
Public Policy Formation and Implementation.'' In William Outhwaite and
Stephen Turner (Eds). \emph{The SAGE Handbook of Political
Sociology}. London, UK: Sage. \\[.2cm]

\subsection*{Edited Special Issues}
\noindent
  \note{2023}David Tindall, Nina Kolleck, and John
McLevey (Guest Journal Editors). ``Social Networks and Anthropogenic
Climate Change.'' Special issue of \emph{Social Networks}.\\[.2cm]
  \note{2020}Mark Stoddart, John McLevey, Vanessa Schweizer, and
Catherine Wong (Guest Journal Editors). ``Climate Change and Energy
Futures.'' Special issue of \emph{Society \& Natural Resources}.\\[.2cm]

% \vspace{-30pt}

\subsection*{Article Manuscripts in Progress}
\noindent
  \note{R\&R}Owen Gallupe, Noam Gidron, John McLevey, and Annika
Hillebrandt. ``Unpacking the crime-generating effect of exclusionary
political rhetoric.'' Revise \& Resubmit, \emph{Criminology}.\\[.2cm]
  \note{In Progress}John McLevey, Tyler Crick, Darrin Durant, and
Karmvir Padda. ``How Political Beliefs Form and Evolve in Interaction
Networks: A Generative Stance Model.'' In Progress.\\[.2cm]
  \note{In Progress}John McLevey. ``A Generative Method for Constructing
and Analyzing Belief Networks from Survey and Text Data.'' In
Progress.\\[.2cm]

\subsection*{Book Manuscripts in Progress}
\noindent
  \note{In Progress}John McLevey. ``Reproducible Research and Generative
Modelling for Social and Cognitive Scientists.'' In Progress.\\[.2cm]

\subsection*{Research \& Policy Reports}
\noindent
  \note{2020}John McLevey, \emph{Pierson Browne}, \emph{Tyler Crick},
and Jillian Anderson. ``Applied Computer Vision for Disinformation
Research: An Analysis of Twitter's Elections Integrity Data on Russian
and Chinese Information Operations.'' Prepared for the Crime \& Security
Research Institute, Cardiff University.\\[.2cm]
  \note{2020}John McLevey, \emph{Pierson Browne}, and \emph{Tyler
Crick}. ``Online Deception \& Dynamic Narrative Networks.'' Prepared for
the Crime \& Security Research Institute, Cardiff University.\\[.2cm]
  \note{2020}Rob Gorbet, Janice Aurini, Jessica Risk, Allyson Stokes,
John McLevey, and \emph{Nicole Figueiredo}. ``The COVID-19 Pandemic and
Canadian Schooling.'' Prepared for Education Onward Council in
consultation with Fair-Chance Learning.\\[.2cm]
  \note{2019}Janice Aurini, Rob Gorbet, John McLevey, Jessica Rizk, and
Allyson Stokes (Alphabetical). ``White Paper on Ed-Tech Connect: An
Intersectoral Workshop on Education, Technology, and
21\textsuperscript{st} Century Labour.'' Funded by SSHRC Connections
Grant.\\[.2cm]
  \note{2017}Janice Aurini, John McLevey, Allyson Stokes, and Rob
Gorbet. ``Classroom Robotics and Acquisition of 21\textsuperscript{st}
Century Competencies: An Action Research Study of Nine Ontario School
Boards.'' Prepared for the Council of Ontario Directors of Education
(CODE) and the Ministry of Education, Ontario.\\[.2cm]


\vspace{.2cm}
\section*{Reviews and Other Short Non-Refereed Publications}
\noindent
  \note{2021}John McLevey. ``Probabilistic Topic Models.'' In Janice
Aurini, Melanie Heath, and Stephanie Howells. 2021. \emph{The How To of
Qualitative Research}. London, UK: Sage.\\[.2cm]
  \note{2019}John McLevey. ``Epistemic and Evidential Cultures.'' In
Paul Atkinson, Sara Delamont, Richard Williams, and Alex Cernat (Eds).
\emph{Sage Research Methods Foundations Online}.\\[.2cm]
  \note{2019}John McLevey. ``Review of David Johnson (2017) \emph{A
Fractured Profession: Commercialization and Conflict in Academic
Science}.'' Baltimore: Johns Hopkins University Press. Review published
in \emph{American Journal of Sociology}. 125(1).\\[.2cm]

\vspace{.2cm}
\section*{Research Grants}

\begin{table}[H]
\raggedleft
\caption*{\raggedleft \emph{Overview of Research Grants Since 2013}}
\input{templates_and_tables/grants.tex}
\end{table}

\noindent
  \note{2020--2025}\textbf{Disinformation, Democracy, and Online
Political Deliberation}\\
  \$219,003 -- \emph{SSHRC Insight Grant}\\
  John McLevey (Principal Investigator), Anabel Quan-Haase, David
Tindall (Co-investigators), Darrin Durant, Deena Abul-Fottouh, Owen
Gallupe, and Martin Innes (Collaborators).\\[.2cm]
  \note{2020--2021}\textbf{Disinformation, Democracy, and Online
Political Deliberation}\\
  \$20,000 -- \emph{Digital Citizenship Initiative, Department of
Canadian Heritage}\\
  John McLevey (Principal Investigator), Anabel Quan-Haase, David
Tindall (Co-investigators), Darrin Durant, Deena Abul-Fottouh, Owen
Gallupe, and Martin Innes (Collaborators).\\[.2cm]
  \note{2020--2025}\textbf{Engaging Science with Philosophy: Best
Practices for Fostering Effective Collaboration}\\
  \$154,406 -- \emph{SSHRC Insight Grant}\\
  Kathryn S. Plaisance (Principal Investigator), Kevin Elliott, Michael
O'Rourke, Lisbeth Berbary, and John McLevey (Collaborators).\\[.2cm]
  \note{2019}\textbf{An Intersectoral Workshop on Education, Technology,
and 21\textsuperscript{st} Century Labour}\\
  \$16,400 + matching funds -- \emph{SSHRC Connection Grant with
Contributions from the University of Waterloo and the Balsillie School
of International Affairs}\\
  Janice Aurini (Principal Investigator), Allyson Stokes, John McLevey,
Jessica Rizk, and Rob Gorbet (Co-investigators).\\[.2cm]
  \note{2018-2019}\textbf{Climate Change and Energy Futures Workshop:
Challenges and Opportunities for Global and Interdisciplinary
Research}\\
  \$24,373 + \$14,399 in matching funds -- \emph{SSHRC Connection Grant
with Contributions from the University of Waterloo and Memorial
University}\\
  Mark Stoddart (Principal Investigator), John McLevey, John Sandlos,
Vanessa Schweizer, and Catherine Wong (Co-investigators).\\[.2cm]
  \note{2016--2022}\textbf{Making Sense of Climate Action: Understanding
Social Mobilization to Curb Anthropogenic Climate Change Through
Advances in Social Network Analysis}\\
  \$282,672 -- \emph{SSHRC Insight Grant}\\
  David Tindall (Principal Investigator), John McLevey, Mark
Stoddart (Co-investigators), Mario Diani, Jennifer Earl, Dana R Fisher,
Philip Leifeld, Andrew Jorgenson, Philippe Le Billon, Don Grant, and
Moses Boudourides (Collaborators).\\[.2cm]
  \note{2016--2020}\textbf{Information and Idea Diffusion in an Open
Source Collaboration Network}\\
  \$150,000 -- \emph{Early Researcher Award (ERA), Ontario Ministry of
Research \& Innovation}\\
  John McLevey (Principal Investigator).\\[.2cm]
  \note{2016--2018}\textbf{Remaking the Boundaries of Open and
Proprietary Science: A Longitudinal Study of Biomedical Research and
Development Networks in Canada}\\
  \$67,790 -- \emph{SSHRC Insight Development Grant}\\
  John McLevey (Principal Investigator), Owen Gallupe, Martin
Cooke (Collaborators).\\[.2cm]
  \note{2016--2918}\textbf{Increasing the Impact of Philosophy of
Science in Scientific Domains}\\
  \$59,302 -- \emph{SSHRC Insight Development Grant}\\
  Kathryn S. Plaisance (Principal Investigator), John
McLevey (Co-investigators).\\[.2cm]
  \note{2015--2016}\textbf{Challenges and Opportunities for Governance
of Socio-Ecological Systems in Comparative Perspective}\\
  \$8,400 -- \emph{BSIA Major Workshops Grant}\\
  John McLevey (Principal Investigator), Vanessa
Schweizer (Co-investigators).\\[.2cm]
  \note{2015--2020}\textbf{The Oil-Tourism Interface and
Social-Ecological Change in the North Atlantic}\\
  \$188,432 -- \emph{SSHRC Insight Grant}\\
  Mark Stoddart (Principal Investigator), John
McLevey (Co-investigators).\\[.2cm]
  \note{2014--2016}\textbf{Collaborative Design in Online Networks}\\
  \$78,814 -- \emph{SSHRC Insight Development Grant}\\
  John McLevey (Principal Investigator).\\[.2cm]
  \note{2013}\textbf{Faculty Research Startup Grant}\\
  \$15,000 -- \emph{University of Waterloo}\\
  John McLevey (Principal Investigator).\\[.2cm]

\vspace{.2cm}
\section*{Teaching Grants}
\noindent
  \note{2015--2016}\textbf{A Data-Driven and Interactive Approach to
Enhancing Student Learning about Disciplinary and Interdisciplinary
Knowledge Production}\\
  \$4,765.20 -- \emph{LITE Seed Grant, Centre for Teaching Excellence,
University of Waterloo}\\
  John McLevey (Principal Investigator).\\[.2cm]

\vspace{.2cm}
\section*{Awards and Selected Scholarships}
\noindent
  \note{2017}\textbf{Outstanding Performance Award}\\
  \emph{University of Waterloo}\\[.2cm]
  \note{2010--2013}\textbf{Bombardier Canada Graduate Scholarship}\\
  \$105,000 -- \emph{SSHRC Doctoral Scholarship (Category A)}\\[.2cm]
  \note{2010--2011}\textbf{Ontario Graduate Scholarship}\\
  \$15,000 (declined) -- \emph{Province of Ontario}\\[.2cm]
  \note{2009--2013}\textbf{PhD Graduate Scholarship}\\
  \$52,000 (declined) -- \emph{McMaster University}\\[.2cm]
  \note{2009--2010}\textbf{Ontario Graduate Fellowship}\\
  \$12,000 + \$3,000 Sociology Department Top Up -- \emph{McMaster
University}\\[.2cm]
  \note{2009}\textbf{University Gold Medal for Excellence in
Sociology}\\
  \emph{Memorial University}\\[.2cm]

\vspace{.2cm}
\section*{Policy Research Contracts}
\noindent
  \note{2020}\textbf{Applied Computer Vision and Ensemble Machine
Learning for Disinformation Research}\\
  John McLevey. Project for the Crime \& Security Research Institute,
Cardiff University.\\[.2cm]
  \note{2020}\textbf{Automated Detection of `Bursty' Concepts, Claims,
and Narratives in Social Media Data}\\
  John McLevey. Project for the Crime \& Security Research Institute,
Cardiff University.\\[.2cm]
  \note{2016--2017}\textbf{Assessing the Impact of Classroom-Integrated
Robotics on the Cultivation of 21\textsuperscript{st} Century
Competencies}\\
  Janice Aurini, John McLevey, and Rob Gorbet. Contract with Council of
Ontario Directors of Education (CODE) for the Ontario Ministry of
Education.\\[.2cm]

\vspace{.2cm}
\section*{(Selected) Scientific Software, Designed and Developed}
\noindent
  \note{\textbf{\texttt{dcss}}}\texttt{dcss} is a Python package
accompanying John McLevey (2022) \emph{Doing Computational Social
Science}. It includes curated datasets and a large collection of utility
functions for data processing and working with statistical and machine
learning models. It is designed, developed, and maintained by John
McLevey, Tyler Crick, Pierson Browne.\\
  License: GNU General Public License 2\\[.2cm]
  \note{\textbf{\texttt{mk}}}\texttt{metaknowledge} (or \texttt{mk}) is
a Python package for quantitative and social networks research in the
sociology of science and information science. First released in 2015.
Under active development. Website and documentation:
\url{http://networkslab.org/metaknowledge/}. It is designed, developed, and maintained by Reid
McIlroy-Young and John McLevey.\\
  License: GNU General Public License 2\\[.2cm]
  \note{\textbf{\texttt{Nate}}}\texttt{Nate} (\textbf{n}etwork
\textbf{a}nalysis with \textbf{te}xt) is a Python package for
network-based text
analysis. It is designed, developed, and maintained by John McLevey,
Pierson Browne, and Tyler Crick.\\
  License: MIT License\\[.2cm]
  \note{\textbf{\texttt{pdpp}}}\texttt{pdpp} is a Python package for
principled data processing with Python. It was first released in 2015
and is under active
development. It is designed, developed, and maintained by Pierson
Browne, Tyler Crick, Rachel Wood, and John McLevey.\\
  License: MIT License\\[.2cm]
  \note{\textbf{\texttt{simkit}}}\texttt{simkit} is a Python package for
probabilistic and agent-based computational models of opinion dynamics,
diffusion, learning, and influence. It is currently in beta and under
active development. It is designed, developed, and maintained by John
McLevey.\\
  License: MIT License\\[.2cm]
  \note{\textbf{\texttt{tidyext}}}\texttt{tidyextractors} is a Python
package for extracting quantitative datasets from source code
repositories, email mbox files, and social media
APIs. It is designed, developed, and maintained by Joel Becker
(NETLAB).\\
  License: MIT License\\[.2cm]
  \note{\textbf{\texttt{gitnet}}}\texttt{gitnet} is a Python package for
mining source code repository and mailing list data and generating
network datasets. First released in 2016. \texttt{gitnet} is still
publicly available and functional, but development and maintenance
efforts have shifted to other Python
packages. It is designed, developed, and maintained by Joel Becker,
Jillian Anderson, Steve McColl, and John McLevey.\\
  License: MIT License\\[.2cm]

\vspace{.2cm}
\section*{Other Contributions to Scientific Software}
\noindent
  \note{\textbf{\texttt{recordlink}}}Contributions to Jonathan de
Bruin's Python package \texttt{recordlinkage}: A Python package for
linking records across multiple data sources when there is no unique ID
available. NetLab contributions were focused on implementing new
comparison and fusion algorithms for my research on the structure and
evolution of cross-sectoral collaboration networks in science and
technology. Most NetLab contributions to \texttt{recordlinkage} were
implemented by Joel Becker (RA) and occasionally Jillian Anderson (RA),
and then submitted to Jonathan de Bruin as pull requests. 
  \\[.2cm]

\vspace{.2cm}
\section*{Conference Presentations}
\noindent
  \note{2022-07}John McLevey. ``Political Polarization and Probabilistic
Belief Network Analysis'' \emph{Sunbelt, Annual meetings of the
International Network for Social Network Analysis}. Melbourne,
Australia.\\[.2cm]
  \note{2019-10}John McLevey. ``Disinformation, Democracy, and Influence
in Online Political Discussion Networks.'' \emph{Disinformation
Symposium, hosted by the Cardiff University Crime \& Security Research
Institute}. Hensol Castle, Vale of Glamorgan, Wales UK.\\[.2cm]
  \note{2019-07}John McLevey. ``What do open online communities of
specialists need tacit knowledge for anyway?'' \emph{SEESHOP}. Helsinki,
Finland.\\[.2cm]
  \note{2019-06}John McLevey, \emph{Alexander Graham}, \emph{Tyler
Crick}, and \emph{Pierson Browne}. ``Measuring Social and Cognitive
Distance in Collaboration Networks Constructed From Observational
Data.'' \emph{Sunbelt, Annual meetings of the International Network for
Social Network Analysis (Session: Advances in Socio-Semantic Network
Analysis)}. Montréal, QC, Canada.\\[.2cm]
  \note{2019-06}Janice Aurini, Allyson Stokes, Jessica Rizk, John
McLevey, and Rob Gorbet. ``How Do Educational Innovations Diffuse and
Persist?'' \emph{Sunbelt, Annual meetings of the International Network
for Social Network Analysis (Session: Networked Innovation)}. Montréal,
QC, Canada.\\[.2cm]
  \note{2019-06}\emph{Pierson Browne}, \emph{Tyler Crick},
\emph{Alexander Graham}, and John McLevey. ``Cognitive Diversity and the
Production of High Impact Science'' \emph{Sunbelt, Annual meetings of
the International Network for Social Network Analysis (Session:
Networked Innovation)}. Montréal, QC, Canada.\\[.2cm]
  \note{2019-06}Janice Aurini, Allyson Stokes, Jessica Rizk, John
McLevey, and Rob Gorbet. ``How Do Educational Innovations Diffuse and
Persist?'' \emph{Canadian Sociological Association Meetings (Session:
Sociology of Education)}. University of British Columbia, Vancouver BC,
Canada.\\[.2cm]
  \note{2019-04}John McLevey. ``Measuring Belief Homophily and Cognitive
Similarity in Social and Political Networks to Advance the Advocacy
Coalition Framework (and Other Policy Theories).'' \emph{Climate Change
and Social Networks Workshop}. Freie Universität Berlin, Berlin,
Germany.\\[.2cm]
  \note{2019-10}Mark Stoddart, Alice Mattoni, and John
McLevey. ``Industrial Development and Eco-Tourisms: Is Co-existence
Possible between Oil Exploration and Nature
Conservation.'' \emph{Department of Geography Blue Box Seminar
Series}. Memorial University, St.~John's, Newfoundland and
Labrador.\\[.2cm]
  \note{2018-10}Mark Stoddart, Alice Mattoni, and John
McLevey. ``Climate Change and Contact Points between Offshore Oil and
Nature-based Tourism in Northern Coastal Societies.'' \emph{Arctic
Circle Assembly}. Reykjavik, Iceland.\\[.2cm]
  \note{2018-06}John McLevey, \emph{Alexander Graham}, and \emph{Pierson
Browne}. ``Remaking the boundaries of open and proprietary science: A
multiple networks analysis of patenting and publishing in biomedical
science'' \emph{Sunbelt, Annual meetings of the International Network
for Social Network Analysis}. Utrecht, Netherlands.\\[.2cm]
  \note{2018-06}\emph{Alexander V. Graham}, \emph{Pierson Browne},
\emph{Jeffery M. Barrett}, and John McLevey. ``RankDir: A New ERGM Term
for Improving Goodness of Fit in Exponential Random Graph Models of
Directed Acyclic Graphs.'' \emph{Sunbelt, Annual meetings of the
International Network for Social Network Analysis}. Utrecht,
Netherlands.\\[.2cm]
  \note{2018-04}John McLevey and \emph{Alexander V. Graham}. ``Smart
Collaboration \& Boundary Spanning for High Impact Climate
Science'' \emph{3rd Spring Campus, University Alliance for
Sustainability}. Freie Universität Berlin. Berlin, Germany.\\[.2cm]
  \note{2017-08}John McLevey. ``Environmental crises, policy, and
scientific change: Insights from a computational model.'' \emph{American
Sociological Association (ASA) annual meeting}. Montréal, QC,
Canada.\\[.2cm]
  \note{2017-06}John McLevey and Reid
McIlroy-Young. ``\texttt{metaknowledge}: open source software for
networks research on science.'' \emph{Sunbelt, Annual meetings of the
International Network for Social Network Analysis}. Beijing,
China.\\[.2cm]
  \note{2017-05}John McLevey. ``Panelist, Assessing Pierre Bourdieu's
Legacy'' \emph{Panel organized by the joint culture/theory research
cluster at the Canadian Sociological Association (CSA) annual
meeting}. Ryerson University. Toronto, ON, Canada.\\[.2cm]
  \note{2017-05}John McLevey, Mark Stoddart, and Yixi Yang. ``The
Oil-Tourism Interface in International Media: A Systematic Comparison of
Norway, Scotland, and Newfoundland and Labrador.'' \emph{Canadian
Sociological Association annual meeting}. Ryerson University. Toronto,
ON, Canada..\\[.2cm]
  \note{2017-05}John McLevey. ``How do face-to-face and virtual networks
shape the development of specialist expertise?'' \emph{SEESHOP}. Geneva,
Switzerland.\\[.2cm]
  \note{2016-08}Vanina Leschziner, John McLevey, and Neil
McLaughlin. ``The American Fame Game: Academic Status and Public Renown
in Post-War Social Sciences.'' \emph{Annual Meetings of the American
Sociological Association (ASA), Section on Science, Knowledge, and
Technology Session}. Seattle, WA, USA.\\[.2cm]
  \note{2016-05}John McLevey. ``Expertise and Experience in Dynamic
Social Networks: Developing A Co-evolution Model for
SEE.'' \emph{SEESHOP}. Cardiff, Wales, UK.\\[.2cm]
  \note{2016-04}John McLevey, Katie Plaisance, Reid McIlroy-Young, and
Alexander Graham. ``Is there a citation penalty for scientifically
relevant philosophy of science?'' \emph{Sunbelt, annual meetings of the
International Network for Social Network Analysis}. Newport Beach,
CA.\\[.2cm]
  \note{2015-11}Owen Gallupe, Sarah Brown, and John McLevey. ``Selection
or Influence? A Meta-Analysis of the Association between Peer and
Personal Offending'' \emph{Annual Meetings of the American Society of
Criminology}. Washington, DC, USA.\\[.2cm]
  \note{2015-08}John McLevey. ``Conflict and Cooperation in Large
Collaboration Networks: An Analysis of Linux Kernel
Development.'' \emph{Annual Meetings of the American Sociological
Association (ASA), Sociology of Technology session}. Chicago,
IL.\\[.2cm]
  \note{2015-06}John McLevey. ``Conflict and Cooperation in Large
Collaboration Networks: An Analysis of Linux Kernel
Development'' \emph{Sunbelt, annual meetings of the International
Network for Social Network Analysis}. Brighton, UK.\\[.2cm]
  \note{2015-05}John McLevey. ``Conflict and Cooperation in Large
Collaboration Networks: An Analysis of Linux Kernel
Development.'' \emph{Annual Meetings of the Canadian Sociological
Association (CSA), Session: Innovation in Social Research: New Data, New
Questions, New Analytics}. Ottawa, ON, Canada.\\[.2cm]
  \note{2015-05}John McLevey, Amelia Howard, Alexander Graham, and
Tiffany Lin. ``Expertise, Stratification, and the Uncertain Democracy of
Large Free / Open Source Developer
Communities.'' \emph{SEESHOP}. Cardiff, Wales, UK.\\[.2cm]
  \note{2014-08}John McLevey. ``Think Tanks in the Space of Opinion:
Tactics for Creating Uncertainty about the Scientific Consensus on
Climate Change.'' \emph{Presented at the Annual Meetings of the American
Sociological Association (ASA)}. San Francisco, CA, USA.\\[.2cm]
  \note{2014-06}John McLevey. ``Struggling Over Climate Expertise:
`Consensus' and `Skepticism' in the Space of Opinion.'' \emph{SEESHOP /
Communities of Integration}. Waterloo, ON, Canada.\\[.2cm]
  \note{2014-05}Allyson Stokes and John McLevey. ``The Invisible
Colleges of Sociology in Canada: A Network Analysis,
1995-2014'' \emph{Annual meetings of the Canadian Sociology Association
(CSA)}. Brock University, St.~Catharines, ON, Canada.\\[.2cm]
  \note{2014-04}John McLevey. ``Funding, Fame, and Politics in the Think
Tank World.'' \emph{The Science Policy Interface: International
Comparisons}. Balsillie School of International Affairs, Waterloo, ON,
Canada.\\[.2cm]
  \note{2014-04}Vanina Leschziner, Neil McLaughlin, and John
McLevey. ``The American Fame Game: Public Renown and Academic Status in
the Social Sciences.'' \emph{Public Intellectuals and Power}. Harvard
University, Cambridge, MA, USA.\\[.2cm]
  \note{2014-08}John McLevey. ``Think Tanks in the Space of Opinion:
Tactics for Creating Uncertainty about the Scientific Consensus on
Climate Change.'' \emph{Annual Meetings of the American Sociological
Association (ASA)}. San Francisco, CA, USA.\\[.2cm]
  \note{2013-10}John McLevey. ``Comments on papers in the session
`Chastened Dreams and New Departures: American Scientific Culture(s) in
Ferment from the 1960s to 1980s''' \emph{Canadian Association of
American Studies (CAAS), Total Money Makeover: Culture and the
Economization of Everything}. Waterloo, ON, Canada.\\[.2cm]
  \note{2013-08}John McLevey. ``How do Think Tanks Produce and Promote
Policy Ideas?'' \emph{Annual Meetings of the American Sociological
Association (ASA), Section: Sociology of Knowledge, Session: Knowledge
and the State}. New York, New York, US.\\[.2cm]
  \note{2013-06}John McLevey. ``Think Tanks on Climate Change: Moral
Views, Scientific Credibility, and Political Contexts'' \emph{Annual
meetings of the Canadian Sociology Association (CSA), Session: The
Sociology of Climate Change}. University of Victoria, Victoria, BC,
Canada.\\[.2cm]
  \note{2013-06}Vanina Leschziner, Neil McLaughlin, and John
McLevey. ``The American Fame Game: Academic Status and Public Renown in
the Social Sciences.'' \emph{Annual meetings of the Canadian Sociology
Association (CSA), Session: The Role of Public Intellectualism in
Academe}. University of Victoria, Victoria, BC, Canada.\\[.2cm]
  \note{2012-05}John McLevey. ``Epistemic Cultures in the Production of
Policy Expertise'' \emph{Qualitative Analysis Conference}. Memorial
University, St John's, NL, Canada.\\[.2cm]
  \note{2012-05}John McLevey. ``Translation Work and the Marketing of
Policy Expertise: Leads from Research on Canadian Think
Tanks.'' \emph{Annual meetings of the Canadian Sociology Association
(CSA), Session: Sociology of Science}. University of Waterloo and
Wilfrid Laurier University, Waterloo, ON, Canada.\\[.2cm]
  \note{2011-08}John McLevey. ``Rhythms and Reason Giving: Understanding
Academic Involvement in Canadian Think Tanks.'' \emph{Annual meetings of
the American Sociology Association (ASA)}. Las Vegas, NV, USA.\\[.2cm]
  \note{2011-04}John McLevey. ``Rhythms and Reason Giving: Understanding
Academic Involvement in Canadian Think Tanks.'' \emph{Invited
Participant, NYLON workshop on ``Cultures of Circulation''}. Ottawa, ON,
Canada.\\[.2cm]
  \note{2011-02}John McLevey. ``Rhythms and Reason Giving: Understanding
Academic Involvement in Canadian Think Tanks.'' \emph{Annual meetings of
the Eastern Sociology Society (ESS), Session: Constructing Workplaces
and Professional Domains}. Philadelphia, PA, US..\\[.2cm]
  \note{2010-05}John McLevey. ``How and Why Do Academics Get Involved
with Think Tanks?'' \emph{Qualitative Analysis Conference}. Wilfrid
Laurier University, Brantford, ON, Canada.\\[.2cm]
  \note{2010-06}John McLevey. ``Contesting Education: A Comparative
Frame Analysis of Opinion Pieces by The Fraser Institute and The
Canadian Centre for Policy Alternatives.'' \emph{Annual meetings of the
Canadian Sociology Association (CSA)}. Concordia University, Montreal
QC, Canada.\\[.2cm]
  \note{2010-06}Lisa Kowalchuk, Neil McLaughlin, John McLevey. ``Public
Intellectual Work: Uses of the Canadian Op-Ed Column'' \emph{Annual
meetings of the Canadian Sociology Association (CSA)}. Concordia
University, Montreal QC, Canada.\\[.2cm]
  \note{2010-05}John McLevey. ``Contesting Education: A Comparative
Frame Analysis of Opinion Pieces by The Fraser Institute and The
Canadian Centre for Policy Alternatives.'' \emph{Annual Qualitative
Analysis Conference}. Wilfrid Laurier University, Brantford, ON,
Canada.\\[.2cm]
  \note{2009-05}John McLevey. ``Understanding Marginality, Ambiguous
Outcomes, and Failure in Social Movements Research and the Sociology of
Ideas.'' \emph{Annual meetings of the Canadian Sociology Association
(CSA)}. Carleton University, Ottawa ON, Canada.\\[.2cm]


\vspace{.2cm}
\section*{Invited Talks}
\noindent
  \note{2022-03}John McLevey. ``Do liberals drink lattes across the
multiverse? Cultural learning, social influence, and mass opinion
polarization.'' \emph{Knowledge Integration Seminar Series}. University
of Waterloo, Waterloo, ON, Canada.\\[.2cm]
  \note{2022-01}John McLevey. ``Reproducibility and Principled Data
Processing for Computational Science.'' \emph{Toronto Data Workshop on
Reproducibility}. Department of Statistical Sciences, University of
Toronto, Toronto, ON, Canada.\\[.2cm]
  \note{2021-11}John McLevey. ``Modelling Meaning: Recent Advances in
Computational Text Analysis and Why They Matter for
Sociology.'' \emph{Department of Sociology Speaker Series}. Memorial
University, St.~John's, NL, Canada.\\[.2cm]
  \note{2019-12}John McLevey. ``Democracies in Crisis? Online Deception,
Disinformation, and Political Polarization.'' \emph{Science and
Technology Studies Seminar Series}. York University, Toronto, ON,
Canada.\\[.2cm]
  \note{2017-11}John McLevey. ``Gender discrimination in open source
software development: findings from a large-scale audit
study.'' \emph{Guest speaker in course ``Gender Equity''}. University of
Waterloo, Waterloo, ON, Canada.\\[.2cm]
  \note{2017-11}John McLevey. ``A Primer on Computational
Sociology.'' \emph{Guest speaker in Sociology Theory grad seminar,
Department of Sociology \& Legal Studies}. University of Waterloo,
Waterloo, ON, Canada.\\[.2cm]
  \note{2017-05}John McLevey. ``Panelist on SSHRC's new data management
policies: what do they mean for your knowledge making
practices?'' \emph{Annual meetings of the Canadian Sociological
Association (CSA)}. Ryerson University, Toronto, ON, Canada.\\[.2cm]
  \note{2016-03}John McLevey. ``Network Structure and the `Chain of
Trust' in Linux Development: Lessons for Working with Data Scraped from
the Web.'' \emph{Guest speaker in Research Methods class, Department of
Sociology}. Wilfrid Laurier University, Waterloo, ON, Canada.\\[.2cm]
  \note{2016-10}John McLevey. ``Open Science and the Uncertain Future of
University-Industry Partnerships in Biomedical Research and
Development.'' \emph{Environment Seminar Series: Open Data, Open
Science. Faculty of Environment}. University of Waterloo, Waterloo, ON,
Canada.\\[.2cm]
  \note{2016-03}John McLevey and Patrick Famaran (UG student). ``Using
Technology to Facilitate Collaboration'' \emph{Centre for Teaching
Excellence Educational Technology Week}. University of Waterloo,
Waterloo, ON, Canada.\\[.2cm]
  \note{2016-03}John McLevey. ``Enhancing Student Learning by Bringing
Data into the Classroom.'' \emph{GREEN TEA speaker series, Faculty of
Environment}. University of Waterloo, Waterloo, ON, Canada.\\[.2cm]
  \note{2014-12}John McLevey. ``Collaborating On-Line: An Analysis of
Communication Networks for Linux Kernel Developers.'' \emph{Waterloo
Institute for Complexity and Innovation (WICI) Speaker
Series}. University of Waterloo, Waterloo, ON, Canada.\\[.2cm]
  \note{2014}John McLevey. ``Where do good ideas come from? A social
network perspective on creativity and innovation.'' \emph{Waterloo
Unlimited}. .\\[.2cm]
  \note{2013-09}John McLevey. ``Think Tanks, Funding, and Politics of
Policy Knowledge.'' \emph{Knowledge Integration Seminar Series, Faculty
of Environment}. University of Waterloo, Waterloo, ON, Canada.\\[.2cm]

\section*{Teaching}
\subsection*{Assigned Courses}
\noindent
\note{Winter 2024}FCIT 607 -- \emph{Data, Methods, and Models for Future
Cities}\\
Seminar, (N) Students
\\[.2cm]
\note{Winter 2024}INTEG 440 -- \emph{Computational Social Science}\\
Seminar, (N) Students
\\[.2cm]
\note{Fall 2023}INTEG 120 -- \emph{The Art and Science of Learning}\\
Lecture, (47) Students
\\[.2cm]
\note{Fall 2022}INTEG 120 -- \emph{The Art and Science of Learning}\\
Lecture, 91 Students
\\[.2cm]
\note{Winter 2022}INTEG 240 -- \emph{Bullshit, Bias, and Bad
Arguments}\\
Lecture, 77 Students
\\[.2cm]
\note{Fall 2021}INTEG 440 -- \emph{Computational Social Science}\\
Seminar, 21 Students
\\[.2cm]
\note{Fall 2021}INTEG 120 -- \emph{The Art and Science of Learning}\\
Lecture, 73 Students
\\[.2cm]
\note{Fall 2021}INTEG 640 / SOC 712 -- \emph{Computational Social
Science}\\
Seminar, 20 Students
\\[.2cm]
\note{Spring 2021}INTEG 640 / SOC 712 -- \emph{Computational Social
Science}\\
Seminar, 14 Students
\\[.2cm]
\note{Winter 2021}INTEG 440 / SOC 440 -- \emph{Computational Social
Science}\\
Seminar, 25 Students
\\[.2cm]
\note{Winter 2021}INTEG 240 / SOC 230 -- \emph{Bullshit, Bias, and Bad
Arguments}\\
Lecture, 39 Students
\\[.2cm]
\note{Fall 2020}INTEG 340 -- \emph{Research Methods and Design}\\
Lecture, 20 Students
\\[.2cm]
\note{Fall 2020}INTEG 120 -- \emph{The Art and Science of Learning}\\
Lecture, 87 Students
\\[.2cm]
\note{Winter 2020}INTEG 420 (B) -- \emph{Senior Honours Project (B)}\\
Project, 20 Students
\\[.2cm]
\note{Winter 2020}INTEG 440 / 640 -- \emph{Computational Social
Science}\\
Seminar, 19 Students
\\[.2cm]
\note{Fall 2019}INTEG 340 -- \emph{Research Methods and Design}\\
Seminar, 20 Students
\\[.2cm]
\note{Fall 2019}INTEG 120 -- \emph{The Art and Science of Learning}\\
Lecture, 89 Students
\\[.2cm]
\note{Winter 2019}INTEG 420 (B) -- \emph{Senior Honours Project}\\
Project, 20 Students
\\[.2cm]
\note{Winter 2019}INTEG 440 / 640 -- \emph{Computational Social
Science}\\
Seminar, 21 Students
\\[.2cm]
\note{Fall 2018}INTEG 420 (A) -- \emph{Senior Honours Project (A)}\\
Project, 27 Students
\\[.2cm]
\note{Fall 2018}INTEG 340 -- \emph{Research Methods and Design}\\
Lecture, 18 Students
\\[.2cm]
\note{Fall 2018}INTEG 120 -- \emph{The Art and Science of Learning}\\
Lecture, 53 Students
\\[.2cm]
\note{Winter 2018}INTEG 420 (B) -- \emph{Senior Honours Project (B)}\\
Project, 27 Students
\\[.2cm]
\note{Winter 2018}INTEG 340 -- \emph{Research Methods and Design}\\
Seminar, 19 Students
\\[.2cm]
\note{Winter 2018}INTEG 475 -- \emph{Big Data and Society}\\
Seminar, 30 Students
\\[.2cm]
\note{Fall 2017}INTEG 420 (A) -- \emph{Senior Honours Project (A)}\\
Project, 28 Students
\\[.2cm]
\note{Winter 2017}INTEG 120 -- \emph{The Art and Science of Learning}\\
Lecture, 47 Students
\\[.2cm]
\note{Fall 2016}INTEG 375 -- \emph{Research Methods and Design}\\
Seminar, 17 Students
\\[.2cm]
\note{Fall 2016}INTEG 120 -- \emph{Disciplines and Integrative
Practices}\\
Lecture, 49 Students
\\[.2cm]
\note{Winter 2016}INTEG 375 -- \emph{Data Visualization}\\
Seminar, 12 Students
\\[.2cm]
\note{Winter 2016}INTEG 275 -- \emph{Research Methods and Design}\\
Lecture, 16 Students
\\[.2cm]
\note{Fall 2015}INTEG 475 -- \emph{Open Science}\\
Seminar, 11 Students
\\[.2cm]
\note{Fall 2015}INTEG 120 -- \emph{Disciplines and Integrative
Practices}\\
Lecture, 43 Students
\\[.2cm]
\note{Winter 2015}INTEG 275 -- \emph{Creativity and Innovation}\\
Lecture, 26 Students
\\[.2cm]
\note{Winter 2015}INTEG 375 / SOC 312 -- \emph{Science and Technology in
Society}\\
Seminar, 20 Students
\\[.2cm]
\note{Fall 2014}INTEG 120 -- \emph{Disciplines and Integrative
Practices}\\
Lecture, 46 Students
\\[.2cm]
\note{Winter 2014}INTEG 375 / SOC 312 -- \emph{Science and Technology in
Society}\\
Seminar, 15 Students
\\[.2cm]
\note{Fall 2013}INTEG 120 -- \emph{Disciplines and Integrative
Practices}\\
Lecture, 55 Students
\\[.2cm]

\subsection*{Reading Courses (Not Assigned)}
\noindent
\note{Spring 2022}\emph{Political Cognition and Polarization}\\
Graduate
\\[.2cm]
\note{Winter 2020}\emph{Network Science}\\
Graduate
\\[.2cm]
\note{Fall 2020}\emph{Political Disinformation and Influence
Operations}\\
Undergraduate
\\[.2cm]
\note{Spring 2018}\emph{Reproducibility and Replication in the
Sciences}\\
Undergraduate
\\[.2cm]
\note{Spring 2018}\emph{Social Network Analysis with Python}\\
Graduate
\\[.2cm]
\note{Winter 2016}\emph{Exploratory Data Analysis and Visualization}\\
Graduate
\\[.2cm]
\note{Winter 2014}\emph{Organizational Theory}\\
Undergraduate
\\[.2cm]
\note{Spring 2014}\emph{Democracy, Science, and the Politics of
Expertise}\\
Undergraduate
\\[.2cm]
\note{Spring 2014}\emph{Sociology of Science}\\
Undergraduate
\\[.2cm]
\note{Spring 2014}\emph{Social Network Analysis with R}\\
Undergraduate
\\[.2cm]
\note{Spring 2014}\emph{Data Visualization}\\
Undergraduate
\\[.2cm]
\note{Spring 2014}\emph{Organizational Theory}\\
Undergraduate
\\[.2cm]
\note{Spring 2014}\emph{Sociology of Organizations: Case Studies}\\
Undergraduate
\\[.2cm]
\note{Spring 2014}\emph{Sociology of Organizations}\\
Undergraduate
\\[.2cm]
\note{Spring 2014}\emph{Applied Network Science}\\
Undergraduate
\\[.2cm]

\vspace{.2cm}
\section*{Student Supervision}

\begin{table}[H]
\raggedleft
\caption*{\raggedleft \emph{Overview of Student Supervision and Committee Membership Since 2013}}
\input{templates_and_tables/student-supervision.tex}
\end{table}

\subsection*{PhD Student Supervision and Dissertation Committee Membership}
\note{In Progress}\emph{Karmvir Padda -- ABD} (Sociology \& Legal
Studies)\\
John McLevey (Supervisor) + Owen Gallupe and Veronica
Kitchen  \\ Expected defence in 2025
\\[.2cm]
\note{In Progress}\emph{Tyler Crick -- ABD} (Sociology \& Legal
Studies)\\
John McLevey (Supervisor) + Owen Gallupe and Peter
Carrington  \\ Expected defence in 2024
\\[.2cm]
\note{In Progress}\emph{Alexander (Sasha) Graham -- ABD} (Sociology \&
Legal Studies)\\
John McLevey (Supervisor) + Owen Gallupe and Peter
Carrington  \\ Expected defence in 2024
\\[.2cm]
\note{In Progress}\emph{Jessica Gill -- ABD} (Sociology \& Legal
Studies)\\
Rashmee Singh (Supervisor) + Andrea Quinlan and John
McLevey  \\ Expected defence in 2025
\\[.2cm]
\note{In Progress}\emph{Geisha Sanchez -- ABD} (Geography \&
Environmental Management)\\
Sarah Burch (Supervisor) + Olaf Weber and John McLevey  \\ Expected
defence in 2024
\\[.2cm]
\note{In Progress}\emph{Mark Shakespear} (Sociology, University of
British Columbia)\\
David Tindall (Supervisor) + K Harrison, A Jorgenson, M Stoddart, and J
McLevey 
\\[.2cm]
\note{In Progress}\emph{Yasmin Koop-Monteiro -- ABD} (Sociology,
University of British Columbia)\\
David Tindall (Supervisor) + Mark Stoddart and John McLevey 
\\[.2cm]
\note{In Progress}\emph{Yixi Yang -- ABD} (Sociology, Memorial
University)\\
Mark Stoddart (Supervisor) + John McLevey and David Tindall 
\\[.2cm]
\note{In Progress}\emph{Keegan Aaron Fernandes} (Electrical and Computer
Engineering)\\
Dan Davison (Supervisor) + David Wang, Rob Gorbet, and John McLevey 
\\[.2cm]
\note{2024}\emph{Emerson LaCroix} (Sociology \& Legal Studies)\\
Janice Aurini (Supervisor) + John McLevey and Stephanie
Howells  \\ Defended 2024-06
\\[.2cm]
\note{2023}\emph{Pierson Browne} (Sociology \& Legal Studies)\\
John McLevey (Supervisor) + Owen Gallupe and Peter
Carrington  \\ Defended 2023-12
\\[.2cm]
\note{2023}\emph{Peter Duggins} (Systems Design Engineering)\\
Chris Eliasmith (Supervisor) + Bryan Tripp, Kerstin Dautenhahn, and John
McLevey 
\\[.2cm]
\note{2022}\emph{Adam Howe} (Sociology, University of British
Columbia)\\
David Tindall (Supervisor) + Catherine Corrigall-Brown, Rima Wilkes, and
John McLevey  \\ Defended 2022-03
\\[.2cm]
\note{2022}\emph{François Lapachelle} (Sociology, University of British
Columbia)\\
Beth Hirsh (Supervisor) + David Tindall and John McLevey  \\ Defended
2022-02
\\[.2cm]
\note{2022}\emph{Julie Cooke} (School of Environment, Enterprise, and
Development)\\
Jennifer Lynes (Supervisor) + Steve Quilley and John
McLevey  \\ Defended 2022-08
\\[.2cm]
\note{2020}\emph{Rod Missaghian} (Sociology \& Legal Studies)\\
Janice Aurini (Supervisor) + Linda Quirke and John McLevey  \\ Defended
2020-10
\\[.2cm]
\note{2019}\emph{Brittany Etmanski} (Sociology and Legal Studies)\\
Janice Aurini (Supervisor) + Owen Gallupe and John McLevey  \\ Defended
2019-09
\\[.2cm]
\note{2019}\emph{Moutasem Zakkar} (Applied Health Sciences)\\
Craig Janes, Samantha Meyer (Supervisor) + Plinio Morita, Daniel
Lizotte, John McLevey  \\ Defended 2019-11
\\[.2cm]
\note{2018}\emph{Noorin Manji} (Sociology \& Legal Studies)\\
Lorne Dawson (Supervisor) + Janice Aurini and John McLevey  \\ Defended
2018-08
\\[.2cm]
\note{2016}\emph{Michael Clarke} (Sociology \& Legal Studies)\\
Kieran Bonner (Supervisor) + David Goodwin and John McLevey  \\ Defended
2016-06
\\[.2cm]

\subsection*{Master of Arts (MA) and Master of Science (MSc) Student Theses}
\note{2024}\emph{Nermeen Zia Islam} (Balsillie School of International
Affairs)\\
Advisory Role: Supervisor
\\[.2cm]
\note{2022}\emph{Svetlana Kopan} (Sociology and Legal Studies)\\
Advisory Role: Committee Member
\\[.2cm]
\note{2018}\emph{Nicholas Brendan, MD} (School of Public Health
Sciences)\\
Advisory Role: Reader
\\[.2cm]
\note{2018}\emph{Sarah Tang} (School of Environment, Enterprise, and
Development)\\
Advisory Role: Committee Member
\\[.2cm]
\note{2018}\emph{Emerson LaCroix} (Sociology and Legal Studies)\\
Advisory Role: Committee Member
\\[.2cm]
\note{2017}\emph{Alexander V. Graham} (Sociology and Legal Studies)\\
Advisory Role: Supervisor
\\[.2cm]
\note{2017}\emph{Junyi (Jill) Wang} (Geography and Environmental
Management)\\
Advisory Role: Reader
\\[.2cm]
\note{2017}\emph{Stuart Anderson} (Anthropology)\\
Advisory Role: Reader
\\[.2cm]
\note{2016}\emph{Chen Chen} (Geography and Environmental Management)\\
Advisory Role: Reader
\\[.2cm]

\subsection*{Supervised Undergraduate Honours Theses \& Design Projects}
\note{2019-2020}\emph{Harrison Lobb} (Knowledge Integration). ``Rogan to
Spencer: Using Discourse Analysis to Diagnose Pathways of Radicalization
From the Mainstream to the Reactionary Right''
\\[.2cm]
\note{2019-2020}\emph{Jessica Clark} (Knowledge Integration). ``Degree
Planning Website for University of Waterloo Students''
\\[.2cm]
\note{2019-2020}\emph{Aidan Power} (Knowledge Integration). ``An
Analysis of Integrating Ethics Into Computer Science Curricula:
Implications for the Cheriton School of Computer Science''
\\[.2cm]
\note{2018-2019}\emph{Jessilyn Wolfe} (Knowledge
Integration). ``Escaping the Office: Developing Escape Room Experiences
to Improve Corporate Small Group Teambuilding''
\\[.2cm]
\note{2018-2019}\emph{Jason Kurian} (Knowledge Integration). ``Pocket
Blues''
\\[.2cm]
\note{2017-2018}\emph{Rachel Wood} (Knowledge Integration). ``Designing
and developing \texttt{mkd3}, software for learning about academic
literature''
\\[.2cm]
\note{2016-2017}\emph{Jillian Anderson} (Knowledge
Integration). ``\texttt{cydr}: An R Package for Cleaning Agricultural
Yield Data''
\\[.2cm]
\note{2015-2016}\emph{Julia Yaroshinsky} (Sociology \& Legal
Studies). ``Top Contributors of the Linux Kernel: Similarities and
Differences''
\\[.2cm]
\note{2014-2015}\emph{Tiffany Lin} (Knowledge Integration). ``Framing
Controversial Internet Technologies: An Exploratory Network Analysis of
TOR''
\\[.2cm]
\note{2014-2015}\emph{Ben Carr} (Knowledge Integration). ``Paradigms,
Learning, and Change in Organizations''
\\[.2cm]
\note{2013-2014}\emph{Christina Minji Chung} (Sociology \& Legal
Studies). ``Organizational Dynamics of Tech Startups in the
Kitchener-Waterloo Region''
\\[.2cm]
\note{2013-2014}\emph{Chelsea Mills} (Knowledge Integration). ``Keep the
Ideas Coming: How startups encourage creativity and what other
organizations can learn from their example''
\\[.2cm]

\subsection*{Highly Qualified Personnel (HQP) Training (Research Positions)}
\note{2023}\strong{Graduate HQP}\\ Karmvir Padda (1 semester), Tyler
Crick (3 semesters), Pierson Browne (3 semesters), Alexander Graham (3
semesters) 
\\[.2cm]
\note{2022}\strong{Graduate HQP}\\ Tyler Crick (3 semesters), Pierson
Browne (3 semesters), Alexander Graham (3 semesters) 
\\[.2cm]
\note{2021}\strong{Graduate HQP}\\ Tyler Crick (3 semesters), Pierson
Browne (3 semesters), Alexander Graham (3 semesters) 
\\[.2cm]
\note{2020}\strong{Graduate HQP}\\ Tyler Crick (3 semesters), Pierson
Browne (3 semesters), Alexander Graham (3
semesters)  \\ \strong{Undergraduate HQP}\\ Alex de Witt (3 semesters),
Alexis Foss Hill (3 semesters), Harrison Lobb (1 semester)
\\[.2cm]
\note{2019}\strong{Graduate HQP}\\ Tyler Crick (3 semesters), Pierson
Browne (3 semesters), Alexander Graham (3
semesters)  \\ \strong{Undergraduate HQP}\\ Alex de Witt (1 semester),
Alexis Foss Hill (1 semester), Jason Kurian (1 semester)
\\[.2cm]
\note{2018}\strong{Graduate HQP}\\ Tyler Crick (3 semesters), Pierson
Browne (3 semesters), Alexander Graham (3 semesters), Yixi Yang (3
semesters), Brittany Etmanski (1 semester), Janet Michaud (1
semester)  \\ \strong{Undergraduate HQP}\\ Mumtahin Monzoor (1
semester), Rachel Wood (2 semesters)
\\[.2cm]
\note{2017}\strong{Graduate HQP}\\ Tyler Crick (3 semesters), Pierson
Browne (3 semesters), Alexander Graham (3 semesters), Yixi Yang (3
semesters), Cathlene Hillier (2 semesters), Janet Michaud (1
semester)  \\ \strong{Undergraduate HQP}\\ Mumtahin Monzoor (1
semester), Jillian Anderson (2 semesters), Joel Becker (2 semesters),
Steve McColl (2 semesters)
\\[.2cm]
\note{2016}\strong{Graduate HQP}\\ Brittany Etmanski (3 semesters),
Pierson Browne (3 semesters), Yixi Yang (3 semesters), Cathlene Hillier
(3 semesters), Amelia Howard (2 semesters), Alexander Graham (3
semesters)  \\ \strong{Undergraduate HQP}\\ Tahnee Prior (2 semesters),
Jillian Anderson (2 semesters), Steve McColl (2 semesters), Joel Becker
(2 semesters), Reid McIlroy-Young (3 semesters)
\\[.2cm]
\note{2015}\strong{Graduate HQP}\\ Amelia Howard (1 semester), Tahnee
Prior (1 semester)  \\ \strong{Undergraduate HQP}\\ Alexander Graham (3
semesters), Tiffany Lin (1 semester), Reid McIlroy-Young (2 semesters)
\\[.2cm]
\note{2014}\strong{Graduate HQP}\\ Janet Michaud (1 semester), Amelia
Howard (3 semesters), Benjamin Nelson (1
semester)  \\ \strong{Undergraduate HQP}\\ Tiffany Lin (1 semester),
Evaleen Hellinga (2 semesters), Alexander V. Graham (3 semesters), 46 KI
students (1 day)
\\[.2cm]
\note{2013}\strong{Graduate HQP}\\ Skaidra Puodziunas (1 semester),
Alexander V. Graham (1 semester), Evaleen Hellinga (1 semester) 
\\[.2cm]


\subsection*{Other Highly Qualified Personnel (HQP) Training (Workshops, Short Courses)}
\note{2024}Instructor for \emph{Introduction to Computational Social
Science with Python} (5 days), GESIS Fall Seminar in Computational
Social Science, Leibniz Institute for the Social Sciences, Cologne
Germany. Course materials co-designed with Johannes Gruber (University
of Amsterdam), who teaches the R course.
\\[.2cm]
\note{2018-Present}Co-Instructor (with Eric Kennedy) for \emph{Science
Outside the Lab (SOtL) North}: a week long intensive course in science
policy held annually in Ottawa and Montréal or Vancouver and Victoria.
Each course cohort is \textasciitilde{} 14 graduate students from
science and engineering disciplines across Canada.
\\[.2cm]
\note{2020}Research Methods Workshop (5 days), GESIS Spring Seminar,
Leibniz Institute for the Social Sciences, Cologne Germany.
\emph{Working with Digital Behavioural Data.} Co-designed and instructed
with Jillian Anderson.
\\[.2cm]
\note{2019}Research Methods Workshop (1 day), Transylvania Summer School
in Research Methods. \emph{Using Network Analysis to (Partially)
Automate Literature Reviews}
\\[.2cm]
\note{2019}Research Methods Workshop (2 days) instructed at University
of British Columbia, Department of Sociology. \emph{Introduction to Big
Data and Automated Text Analysis for Social Scientists}
\\[.2cm]
\note{2019}Research Methods Workshop (2 days) instructed at University
of Waterloo. \emph{(Partially) Automating Literature Reviews for
Knowledge Synthesis and Discovery}
\\[.2cm]
\note{2019}Research Methods Workshop (2 days) instructed at University
of Waterloo. \emph{How to Analyze Networks with R}
\\[.2cm]
\note{2019}Research Methods Workshop (1 day) instructed at University of
Waterloo. \emph{Automated Content Analysis for Social Scientists}
\\[.2cm]

\section*{Service -- To the Profession}

\noindent
  \note{2019-2023}Co-organizer (with Rochelle Côté) and liaison with the
Canadian Sociological Association for the Social Networks Research
Cluster.\\[.2cm]
  \note{2016-2019}Communications Officer, Executive Council Member,
Canadian Sociological Association.\\[.2cm]
  \note{2019}Member of the Scientific Committee for Sunbelt XXXIX
Conference in Montréal, International Network for Social Network
Analysis (INSNA).\\[.2cm]
  \note{2014-2019}Organizer and liaison with the Canadian Sociological
Association for the Sociology of Science, Technology, and Knowledge
Research Cluster.\\[.2cm]

\subsection*{Peer Reviewing - Academic Journals}
\begin{itemize}[noitemsep]
      \item \emph{Nature Communications}
      \item \emph{American Journal of Sociology}
      \item \emph{American Sociological Review}
      \item \emph{Social Networks}
      \item \emph{Canadian Review of Sociology}
      \item \emph{Science and Public Policy}
      \item \emph{Scientometrics}
      \item \emph{Sociological Theory}
      \item \emph{Social Studies of Science}
      \item \emph{Canadian Journal of Sociology}
      \item \emph{Methodological Innovations}
      \item \emph{Acta Sociologica}
      \item \emph{Society \& Natural Resources}
  \end{itemize}

\subsection*{Peer Reviewing - Books}
\begin{itemize}[noitemsep]
      \item 1 book manuscript for Sage, UK. Quantitative research
methods series.
      \item 1 book manuscript for Sage, UK. Quantitative research
methods series.
  \end{itemize}

\subsection*{Peer Reviewing / Evaluation - Grants}
    \note{2022}Peer Reviewer for the 2022 SSHRC Insight Grant Awards
Competition (Multi-disciplinary).\\[.2cm]
    \note{2019}Peer Reviewer for the 2019 SSHRC Insight Grant Awards
Competition (Multi-disciplinary).\\[.2cm]
    \note{2018}Evaluator for 2017 SSHRC Insight Development Grants
Competition.\\[.2cm]
    \note{2017}Observer for the 2018 SSHRC Postdoctoral Awards
Competition.\\[.2cm]
  
\subsection*{Peer Reviewing - Other}
    \note{2020}Chapter for Luke Sloan and Anabel Quan-Haase (eds).
\emph{The SAGE Handbook for Social Media Research Methods},
2\textsuperscript{nd} edition. London: Sage.\\[.2cm]
    \note{2020}Sage Campus Course. (Online research design
classes)\\[.2cm]
    \note{2018}Sage Campus Course. (Online research design
classes)\\[.2cm]
  
\subsection*{Conference Sessions Organized}
\noindent
  \note{2024}Sessions on \emph{Network Approaches to Attitudes and
Beliefs} at the 2024 Sunbelt meetings in Edinburgh, Scotland.
Co-organized with Claudia Zucca, Mario Diani, and Lorien Jasny.\\[.2cm]
  \note{2022}Sessions on \emph{Social Networks and Climate Change} at
the 2022 Sunbelt meetings in Melbourne, Australia. Co-organized with
David Tindall and Mark Stoddart.\\[.2cm]
  \note{2020}Sessions on \emph{Disinformation}, \emph{Computational
Methods}, \emph{Climate Change}, and \emph{Social Movements} at the 2020
Sunbelt meetings in Paris, France (held remotely).\\[.2cm]
  \note{2019}\emph{Social Networks and Sociology} panel (with
Dr.~Rochelle Côté), CSA.\\[.2cm]
  \note{2019}Sessions for \emph{Social Networks} Research Cluster,
CSA.\\[.2cm]
  \note{2019}Sessions for \emph{Sociology of Science, Technology, and
Knowledge} Research Cluster, CSA.\\[.2cm]
  \note{2017}\emph{Practical Advice on Communicating Sociological
Research} panel, CSA.\\[.2cm]
  \note{2017}\emph{Sociology of Science and Knowledge}, CSA.\\[.2cm]
  \note{2016}\emph{Sociology of Science and Knowledge}, CSA.\\[.2cm]
  \note{2015}\emph{Political Sociology of Science}, CSA.\\[.2cm]
  \note{2015}\emph{Sociology of Science}, CSA.\\[.2cm]
  \note{2014}\emph{Sociology of Technology}, CSA.\\[.2cm]
  \note{2014}\emph{Sociology of Culture} (with Dr.~Allyson Stokes),
CSA.\\[.2cm]

\section*{Service -- University of Waterloo}
\noindent
  \note{2022-2023}Knowledge Integration Department Chair Search and
Selection Committee\\[.2cm]
  \note{2023-Present}Associate Chair (Undergraduate), Department of
Knowledge Integration. (\emph{Vanessa Schweizer is interim Associate
Chair while I am on parental leave}.)\\[.2cm]
  \note{2022 (07-12)}Associate Chair (Undergraduate), Department of
Knowledge Integration.\\[.2cm]
  \note{2021-2022}Member of the Administrative Committee, Faculty of
Environment.\\[.2cm]
  \note{2021-2022}Chair of the Environment Faculty Council, Faculty of
Environment.\\[.2cm]
  \note{2019-Present}Liaison between the Faculty of Environment and the
Cybersecurity and Privacy Institute, University of Waterloo.\\[.2cm]
  \note{2020-2022}Faculty Association University of Waterloo (FAUW),
Member of Council of Representatives, Department of Knowledge
Integration.\\[.2cm]
  \note{2019}Committee member, Tenure and Promotions Committee,
Department of Knowledge Integration.\\[.2cm]
  \note{2018}Search and selection committee member for two Canada
Research Chairs in Environment and Sustainability, Faculty of
Environment.\\[.2cm]
  \note{2018}Panelist on the SSHRC Insight Development Grants Panel,
organized by Ruth Knechtel from the University of Waterloo Office of
Research.\\[.2cm]
  \note{2017-2018}Committee member for university-level `Research
excellence and crossing disciplinary lines' committee, which developed a
white paper to inform the development of the next University of Waterloo
strategic plan. Part of my contribution included a network analysis of
inter- and intra-faculty collaboration networks on campus.\\[.2cm]
  \note{2016}Informal committee designing a Master's in Data Science at
the University of Waterloo, joint initiative of the Faculty of Arts and
Faculty of Environment.\\[.2cm]
  \note{2016-2019}Member of Communications Outcomes Committee in the
Faculty of Environment.\\[.2cm]
  \note{2016}Internal External Examiner for PhD Dissertation in the
Department of Applied Mathematics, University of Waterloo. John Lang,
`Mathematical Modelling of Social Factors in Decision Making Processes
at the Individual and Population Levels.' Dissertation Supervisors: Drs.
Hans De Sterck and Daniel M. Abrams.\\[.2cm]
  \note{2016}Internal External Examiner for PhD Dissertation in the
Department of Philosophy, University of Waterloo. Benjamin Nelson, `The
Depictions of Unwritten Law.' Committee Members: Brian Orend, Heather
Douglas, and Matt Doucet.\\[.2cm]
  \note{2016-Present}Member of the University of Waterloo Task Force on
Bibliometrics.\\[.2cm]
  \note{2016-2017}Committee Member on the Faculty of Environment
Committee on the University of Waterloo HeForShe Campaign to make gender
equality a top institutional priority.\\[.2cm]
  \note{2016}Co-organized (with Ian Milligan) a Software Carpentry
workshop at the University of Waterloo focusing on shell scripting, git,
and Python for social scientific and historical research.\\[.2cm]
  \note{2016-2021}Faculty Advisor, University of Waterloo iGEM
(International Genetically Engineered Machine) Team, Policy \& Practices
Subgroup, Mathematical Modeling Subgroup (occasionally). 2016 Gold Medal
Winners.\\[.2cm]
  \note{2014-Present}Board Member, University of Waterloo Survey
Research Centre\\[.2cm]
  \note{2014-2015}Faculty of Environment representative on the Arts
Faculty Council\\[.2cm]
  \note{2014-2017}Department of Knowledge Integration representative on
the Environment Faculty Council\\[.2cm]
  \note{2014-2015}Member of the English Language Competency Committee in
the Faculty of Environment\\[.2cm]
  \note{2014}Faculty of Environment Teaching and Learning
Committee\\[.2cm]
  \note{2014}Internal External Examiner for PhD Dissertation in the
Department of Psychology, University of Waterloo. Nathaniel Barr,
`Reasoned connections: Complex creativity and dual-process theories of
cognition.' Dissertation Advisor: Jonathon Fugelsang.\\[.2cm]

\section*{Service -- McMaster University}
\noindent
  \note{2011-2012}Selection Committee member for two tenure-track hires
in Sociology\\[.2cm]
  \note{2010-2012}Chair of Graduate Student Caucus\\[.2cm]
  \note{2011-2012}PhD (ABD) Representative on the Graduate
Committee\\[.2cm]
  \note{2009-2010}PhD Representative on the Graduate Committee\\[.2cm]
  \note{2009-2010}Co-Organizer, Culture and Politics workshop\\[.2cm]
  \note{2009-2012}Co-Organizer of Jane Synge Memorial
Conferences\\[.2cm]
  \note{2009-2012}Peer Mentor in Sociology Peer Mentoring
Program\\[.2cm]
  \note{2008-2009}Union Steward, Sociology (CUPE 3906)\\[.2cm]

\section*{Additional Training and Professional Development}
\noindent
  \note{2023-2024}\emph{Academic Leadership for New Department Chairs
and Associate Chairs}, Academic Leadership Program, University of
Waterloo. Sessions include: Planning and Prioritizing for Change;
Performance Conversations; Marketing, Recruitment, and Admissions;
Governance and Policy at UW; Decreasing Unhealthy Conflict and
Increasing Healthy Conflict; etc.\\[.2cm]
  \note{2016}Technical / methods workshops attended at Sunbelt 2016,
Newport Beach, USA: (1) Understanding Diffusion with netdiffuseR, (2)
Moving beyond Descriptives: Basic Network Statistics with statnet, (3)
Exponential Family Random Graph Modeling (ERGMs) Using statnet, (4)
Introduction to Egocentric Network Data Analysis with ERGMs and TERGMs
Using \texttt{statnet}\\[.2cm]
  \note{2015}Technical / methods workshops attended at Sunbelt 2015,
Brighton, UK: (1) Networks in Python: The \texttt{networkx} Package,
Parts 1 \& 2, (2) Mining of large social networks from Twitter, Facebook
and LinkedIn using Python, (3) Social Network Approaches for Behavior
Change, (4) Visualizing Social Networks. How to Create Meaningful and
Compelling Network Drawings.\\[.2cm]
  \note{2012}Qualitative Comparative Analysis and Fuzzy Sets. Arizona
Methods Workshops, held at University of Arizona.\\[.2cm]
  \note{2011}Hierarchical Linear Models. Inter-University Consortium for
Political and Social Research (ICPSR), held at University of
Massachusetts, Amherst.\\[.2cm]

\section*{Research and Teaching Assistantships (2008-2013)}
\noindent
  \note{2010-2013}Research Assistant for Neil McLaughlin, Sociology,
McMaster University. `\emph{Shaping Opinion in the Public Sphere: Public
Intellectual Authority in the Journalistic Field},' Funded by SSHRC
Standard Research Grant.\\[.2cm]
  \note{2009-2010}Teaching Assistant for Classical and Contemporary
Sociological Theory. Neil McLaughlin, Sociology, McMaster
University.\\[.2cm]
  \note{2008-2009}Research Assistant for Neil McLaughlin, Sociology,
McMaster University. `\emph{Professors as Public Intellectuals},' Funded
by SSHRC Standard Research Grant.\\[.2cm]

\section*{Professional Memberships}
\noindent
Canadian Sociological Association (CSA), American Sociological
Association (ASA), International Network for Social Network Analysis
(INSNA), Network Science Society (NetSci), International Sociological
Association (ISA), European Consortium for Political Research (ECPR)

\end{document}
