\noindent Knowledge Integration, Sociology \& Legal Studies\\
\noindent University of Waterloo, Waterloo, ON, Canada\\
\noindent \href{http://www.johnmclevey.com}{johnmclevey.com} \textbar{}
\href{http://networkslab.org}{networkslab.org}\\
\noindent john.mclevey@uwaterloo.ca\\
\noindent 647-921-2044\\
\bigskip
\noindent Citizenship: Canadian

\section{Appointments}\label{appointments}

\ind 2013-Present. Assistant Professor, University of Waterloo\\
\href{https://uwaterloo.ca/knowledge-integration/}{Department of
Knowledge Integration},
\href{https://uwaterloo.ca/sociology-and-legal-studies/}{Department of
Sociology and Legal Studies}\\
\href{https://uwaterloo.ca/graduate-studies/about-graduate-studies/organization-graduate-studies\#6}{Approved
Doctoral Dissertation Supervisor (ADDS) Status}

\section{Affiliations}\label{affiliations}

\ind 2014-Present. Affiliate Researcher,
\href{http://wici.ca/new/}{Waterloo Institute for Complexity and
Innovation}

\ind 2014-Present. Board Member,
\href{http://math.uwaterloo.ca/survey-research-centre/node/1}{University
of Waterloo Survey Research Centre}

\ind 2014-Present. Fellow,
\href{http://www.balsillieschool.ca/}{Balsillie School of International
Affairs}

\ind 2014-Present. Cross-appointed to the
\href{https://uwaterloo.ca/environment-resources-and-sustainability/}{School
of Environment, Resources, and Sustainability}

\ind 2016-Present. Cross-appointed to the
\href{https://uwaterloo.ca/geography-environmental-management/}{Department
of Geography and Environmental Management}

\section{Education}\label{education}

\ind 2013. PhD, Sociology, McMaster University. Hamilton, ON, Canada.\\
\ind 2009. MA, Sociology, McMaster University. Hamilton, ON, Canada.\\
\ind 2008. BA Honors, Sociology, Political Science, Memorial University.
St.~John's, NL, Canada.

\section{Research Areas}\label{research-areas}

Computational Social Science, Social Networks, Sociology of Science,
Environmental Sociology, Political Sociology and Social Movements,
Research Methods, Sociology of Education

\section{Peer Reviewed Publications}\label{peer-reviewed-publications}

\subsection{Books / Research
Monographs}\label{books-research-monographs}

\ind Mark Stoddart, Alice Mattoni, and John McLevey. \emph{Industrial Development and Eco-Tourisms: Is Co-existence Possible Between Oil Exploration and Nature Conservation?} Under contract with Palgrave MacMillan.

\subsection{Peer Reviewed Journal Articles and Chapters in Peer Reviewed
Edited
Volumes}\label{peer-reviewed-journal-articles-and-chapters-in-peer-reviewed-edited-volumes}

\footnotesize{\ind Italics = student at time of publication}\bigskip
\normalsize

\ind Owen Gallupe, John McLevey, and Sarah Brown. Forthcoming. ``Selection or Influence? A Meta-Analysis of the Association between Peer and Personal Offending.'' \emph{Journal of Quantitative Criminology}.

\ind John McLevey, \emph{Alexander Graham}, \emph{Reid McIlroy-Young}, \emph{Pierson Browne}, and Kathryn S. Plaisance. 2018. ``Interdisciplinarity and Insularity in the Diffusion of Knowledge: An Analysis of Disciplinary Boundaries Between Philosophy of Science and the Sciences.'' \emph{Scientometrics}. Issue number not yet assigned.

\ind John McLevey and \emph{Ryan Deschamps}. 2018. ``The Sociology of Public Policy Formation and Implementation.'' William Outhwaite and Stephen Turner (eds) \emph{The SAGE Handbook of Political Sociology}. SAGE.

\ind John McLevey, Allyson Stokes, and \emph{Amelia Howard}. 2018. ``Pierre Bourdieu's Uneven Influence on Anglophone Canadian Sociology.''Thomas Medvetz and Jeff Sallaz (eds) \emph{The Oxford Handbook of Pierre Bourdieu}. Oxford: Oxford University Press.

\ind John McLevey and \emph{Reid McIlroy-Young}. 2017. ``Introducing \emph{metaknowledge}: Software for Computational Research in Information Science, Network Analysis, and Science of Science.'' \emph{The Journal of Informetrics}. 11: 176-197.


\ind Allyson Stokes and John McLevey (equal authors). 2016. ``From Porter to Bourdieu: The Evolving Specialty Structure of English Canadian Sociology, 1966- 2014.'' \emph{Canadian Review of Sociology / Revue canadienne de sociologie}. 53(2):176--202.

\ind John McLevey. 2015. ``Understanding Policy Research in Liminal Spaces: Think Tank Responses to Diverging Principles of Legitimacy.''\emph{Social Studies of Science}. 45(2):270-293.

\ind John McLevey. 2014. ``Think Tanks, Funding, and the Politics of Policy Knowledge in Canada.'' \emph{Canadian Review of Sociology / Revue canadienne de sociologie}. 51(1):54-75.

\subsection{Articles In Progress}\label{articles-in-progress}

\ind John McLevey, \emph{Pierson Browne}, and \emph{Alexander Graham}.
``Remaking the Boundaries of Open and Proprietary Science: A Linked Data
Analysis of Multi-Institutional Collaboration in International
Biomedical Science.''

\ind John McLevey, \emph{Alexander Graham}, and \emph{Pierson Browne}.
``Network Structure and the `Chain of Trust' in Free/Libre Open Source
Software Development: The Case of Linux.''

\ind \emph{Alexander Graham} and John McLevey. ``Collective Intelligence
and Diversity Bonuses in Scientific Fields.''

\ind John McLevey, Mark Stoddart, and \emph{Yixi Yang}. ``The
Oil-Tourism Interface in International Media: A Systematic Comparison of
Norway, Scotland, and Newfoundland and Labrador.''

\ind John McLevey and \emph{Alexander Graham}. ``Smart Collaboration \&
Boundary Spanning for High Impact Science.''

\section{Policy Reports}\label{policy-reports}

\ind Janice Aurini, John McLevey, Allyson Stokes, and Rob Gorbet. 2017.
``Classroom Robotics and Acquisition of 21st Century Competencies: An
Action Research Study of Nine Ontario School Boards.'' Report for the
Council of Ontario Directors of Education (CODE) and the Ministry of
Education, Ontario.

\section{Research Grants}\label{research-grants}

\ind Total Research Grants since 2013: \textbf{\$860,740} \bigskip

\ind 2018-2019. Mark Stoddart (PI), \textbf{John McLevey},
(Co-Applicant), John Sandlos (Co-Applicant), Vanessa Schweizer
(Co-Applicant), Catherine Mei Ling Wong (Co-Applicant). Climate Change
and Energy Futures Workshop: Challenges and Opportunities for Global and
Interdisciplinary Research.
\href{http://www.sshrc-crsh.gc.ca/funding-financement/programs-programmes/connection_grants-subventions_connexion-eng.aspx}{SSHRC
Connection Grant}, \$24,373 (plus \$14,339 in matching funds from
Memorial University and University of Waterloo).

\ind 2016-2022. David Tindall (PI), \textbf{John McLevey (Co-I)}, Mark
Stoddart (Co-I). Collaborators: Mario Diani, Jennifer Earl, Dana R
Fisher, Philip Leifeld, Andrew Jorgenson, Philippe Le Billon, Don Grant,
Moses Boudourides.
\href{http://www.sshrc-crsh.gc.ca/funding-financement/programs-programmes/insight_grants-subventions_savoir-eng.aspx}{Social
Science and Humanities Research Council of Canada (\textbf{SSHRC}),
Insight Grant} Application. ``Making sense of climate action:
Understanding social mobilization to curb anthropogenic climate change
through advances in social network analysis,'' \$282,672

% \ind 2016-2020 \textbf{John McLevey (PI)}, Ontario
% \href{https://www.ontario.ca/document/ontario-research-fund-early-researcher-awards-program-guidelines}{Early
% Researcher Award}, Ministry of Research and Innovation, ``Information
% and Idea Diffusion in an Open Source Collaboration Network,'' \$150,000.

\ind 2016-2018 \textbf{John McLevey (PI)}, Owen Gallupe (Collaborator)
and Martin Cooke (Collaborator),
\href{http://www.sshrc-crsh.gc.ca/funding-financement/programs-programmes/insight_development_grants-su\%20bventions_de_developpement_savoir-eng.aspx}{Social
Science and Humanities Research Council of Canada (\textbf{SSHRC})},
Insight Development Grant, ``Remaking the Boundaries of Open and
Proprietary Science: A Longitudinal Study of Biomedical Research and
Development Networks in Canada'' \$67,790.

\ind 2016-2018 Katie Plaisance (PI) and \textbf{John McLevey (Co-I)},
\href{http://www.sshrc-crsh.gc.ca/funding-financement/programs-programmes/insight_development_grants-su\%20bventions_de_developpement_savoir-eng.aspx}{Social
Science and Humanities Research Council of Canada (\textbf{SSHRC})},
Insight Development Grant, ``Increasing the Impact of Philosophy of
Science in Scientific Domains'', \$59,302

\ind 2015-2016 \textbf{John McLevey (PI)} and Vanessa Schweizer (Co-I),
Basillie School of International Affairs, Major Workshops Grant,
``Challenges and Opportunities for Governance of Socio-Ecological
Systems in Comparative Perspective,'' \$8,400.

\ind 2015-2020 Mark Stoddart (PI) and \textbf{John McLevey (Co-I)},
\href{http://www.sshrc-crsh.gc.ca/funding-financement/programs-programmes/insight_development_grants-su\%20bventions_de_developpement_savoir-eng.aspx}{Social
Science and Humanities Research Council of Canada (\textbf{SSHRC})},
Insight Grant, ``The Oil-Tourism Interface and Social-Ecological Change
in the North Atlantic,'' \$188,423.

\ind 2014-2016 \textbf{John McLevey (PI)},
\href{http://www.sshrc-crsh.gc.ca/funding-financement/programs-programmes/insight_development_grants-su\%20bventions_de_developpement_savoir-eng.aspx}{Social
Science and Humanities Research Council of Canada (\textbf{SSHRC}),
Insight Development Grant}, ``Collaborative Design in Online Networks,''
\$74,814.

\ind 2013 University of Waterloo, Faculty Research Startup Grant,
\$15,000.

\section{Teaching Grants}\label{teaching-grants}

\ind 2015-2016 John McLevey (PI), LITE Seed Grant, Center for Teaching
Excellence, University of Waterloo, ``A Data-Driven and Interactive
Approach to Enhancing Student Learning about Disciplinary and
Interdisciplinary Knowledge Production,'' \$4,765.20.

\section{Awards and Selected
Scholarships}\label{awards-and-selected-scholarships}

\ind 2017. Outstanding Performance Award. University of Waterloo.

\ind 2010--2013.
\href{http://www.sshrc-crsh.gc.ca/funding-financement/programs-programmes/fellowships/doctoral-doctorat-eng.aspx}{Joseph-Armand Bombardier Canada Graduate Scholarship},
Category A, SSHRC Doctoral Scholarship, \$105,000.

\ind 2010--2011. Ontario Graduate Scholarship, \$15,000. Declined.

\ind 2009--2013. PhD Graduate Scholarship, McMaster University,
\$52,000. Declined. (\$10,000 replaced by Ontario Graduate Fellowship in
2009--2010, replaced by SSHRC CGS 2010--2013)

\ind 2009--2010. Ontario Graduate Fellowship, \$12,000. Sociology
Department Top Up, \$3,000.

\ind 2009. University Gold Medal for Academic Excellence in Sociology,
Memorial University.

\section{Policy Research Contracts}\label{policy-research-contracts}

\ind 2016-2017. Janice Aurini (Co-PI), John McLevey (Co-PI), Rob Gorbet
(Co-I). ``Assessing the Impact of Classroom-Integrated Robotics on the
Cultivation of 21\textsuperscript{st} Century Competencies.'' Contract
with Council of Ontario Directors of Education (CODE) for the Ontario
Ministry of Education.

\section{Open Source Research
Software}\label{open-source-research-software}

\ind \href{http://networkslab.org/metaknowledge/}{\emph{metaknowledge}}:
A Python package for quantitative and social networks research in the
sociology of science and information science. Developed by Reid
McIlroy-Young and John McLevey. First released in 2015. Under active
development. Website and documentation:
\url{http://networkslab.org/metaknowledge/}.

\ind \href{http://networkslab.org/tidyextractors/}{\emph{tidyextractors}}:
A Python package for extracting quantitative datasets from source code
repositories, email mbox files, and social media APIs (currently
Twitter). Developed and maintained by NetLab RA Joel Becker with NetLab
support. Website and documentation:
\url{http://networkslab.org/tidyextractors/}

\ind Contributions to Jonathan de Bruin's Python package
\href{https://github.com/J535D165/recordlinkage}{\emph{recordlinkage}}:
A Python package for linking records across multiple data sources when
there is no unique ID available. NetLab contributions are focused on
implementing new comparison and fusion algorithms that are necessary for
advancing my grant-funded empirical research on the structure and
evolution of cross-sectoral collaboration networks in science and
technology. Most NetLab contributions to \emph{recordlinkage} are
implemented by Joel Becker (RA) and occasionally Jillian Anderson (RA),
and then submitted to Jonathan de Bruin as pull requests.

\ind \href{http://networkslab.org/gitnet/}{\emph{gitnet}}: A Python
package for mining source code repository and mailing list data and
generating network datasets. Developed by Joel Becker, Jillian Anderson,
Steve McColl, and John McLevey. First released in 2016. \emph{gitnet} is
still publicly available and functional, but development efforts and
maintenance have shifted to \emph{tidyextractors} and other Python
packages. Website and documentation:
\url{http://networkslab.org/gitnet/}

\section{Op-Eds, Public Talks, Non-Reviewed
Writing}\label{op-eds-public-talks-non-reviewed-writing}

\ind John McLevey. 2019. Review of David Johnson (2017) \emph{A
Fractured Profession: Commercialization and Conflict in Academic
Science}. Baltimore: Johns Hopkins University Press. Review published in
\emph{American Journal of Sociology}. 125(1).

\ind Allyson Stokes and John McLevey. 2017. ``The Cultural Sociology
Research Cluster in the Canadian Sociological Association and the CSA
2017 Annual Meeting.'' Newsletter of the Culture Section of the American
Sociological Association.

\ind Occasional technical blog posts on the
\href{http://networkslab.org/}{NetLab blog}

\ind Comments at \emph{XMD} Graduate Students Symposium, Big Data \&
Society. organized by Dr.~Beth Coleman, University of Waterloo. Critical
Media Lab, Kitchener Waterloo, April 9, 2017.

\ind Comments at \emph{Talk Science} event, organized by students and
local community members involved with \emph{Evidence for Democracy}.
Waterloo, ON. September 28, 2015.

\ind ``\href{http://bit.ly/1ohSn1N}{Tory war on evidence claims another
casualty}'' with Liam Swiss. \emph{Toronto Star} Op-Ed published on
September 24 2014, section A15.

\section{Conference Presentations}\label{conference-presentations}

\ind April 2018. John McLevey and Alexander Graham. ``Smart
Collaboration \& Boundary Spanning for High Impact Climate Science.''
3rd Spring Campus, University Alliance for Sustainability. Freie
Universität Berlin. Berlin, Germany.

\ind August 2017 John McLevey. ``Environmental crises, policy, and
scientific change: Insights from a computational model.'' Presented at
the annual American Sociological Association meetings, Montréal, QC,
Canada.

\ind June 2017 John McLevey and Reid McIlroy-Young.
``\emph{metaknowledge}: open source software for networks research on
science'' Presented at the annual Sunbelt meeting, International Network
for Social Network Analysis (INSNA), Beijing, China.

\ind May 2017 John McLevey. Panelist in ``Assessing Pierre Bourdieu's
Legacy,'' organized by the joint culture/theory research cluster
committee at the Canadian Sociological Association meetings at Ryerson
University. Toronto, ON, Canada.

\ind May 2017 John McLevey, Mark Stoddart, and Yixi Yang. ``The
Oil-Tourism Interface in International Media: A Systematic Comparison of
Norway, Scotland, and Newfoundland and Labrador.'' Presented at the
Canadian Sociological Association annual meeting. Toronto, ON, Canada.

\ind May 2017 John McLevey. ``How do face-to-face and virtual networks
shape the development of specialist expertise?'' Presented at SEESHOP
2017, Geneva, Switzerland.

\ind August 2016 Vanina Leschziner, John McLevey, and Neil McLaughlin.
``The American Fame Game: Academic Status and Public Renown in Post-War
Social Sciences.'' Presented at the Annual Meetings of the American
Sociological Association, Section on Science, Knowledge, and Technology
session, Seattle, WA.

\ind May 2016 ``Expertise and Experience in Dynamic Social Networks:
Developing A Co-evolution Model for SEE.'' Presented at
\href{http://www.cf.ac.uk/socsi/contactsandpeople/harrycollins/expertise-project/seeshophome.html}{SEESHOP
9} (Studies of Expertise and Experience), Cardiff Wales, UK.

\ind April 2016 Kirsten Wright, Owen Gallupe, and John McLevey.
``DrugAgent: Measuring the Effect of Restrictive Deterrence on the
Resilience of Agent Based Drug Markets.'' Presented at the
\href{https://www.ineteconomics.org/community/events/complexity-for-new-economic-thinking}{Fields
Institute} ``YSI Complexity and Economics Workshop.'' Toronto, ON,
Canada.

\ind April 2016 John McLevey, Katie Plaisance, Reid McIlroy-Young, and
Alexander Graham. ``Is there a citation penalty for scientifically
relevant philosophy of science?'' Presented by John McLevey and
Alexander Graham at Sunbelt XXXVI (Annual meetings of the International
Network for Social Network Analysis), Newport Beach, CA.

\ind November 2015 Owen Gallupe, Sarah Brown, and John McLevey.
``Selection or Influence? A Meta-Analysis of the Association between
Peer and Personal Offending.'' Presented at the Annual Meetings of the
American Society of Criminology, Washington, D.C.

\ind August 2015 ``Conflict and Cooperation in Large Collaboration
Networks: An Analysis of Linux Kernel Development.'' Presented at the
Annual Meetings of the American Sociological Association, Chicago, IL.
Session: Sociology of Technology.

\ind June 2015 ``Conflict and Cooperation in Large Collaboration
Networks: An Analysis of Linux Kernel Development.'' Presented at
Sunbelt meetings, International Network for Social Network Analysis
(INSNA), Brighton, UK.

\ind May 2015 ``Conflict and Cooperation in Large Collaboration
Networks: An Analysis of Linux Kernel Development.'' Presented at the
Annual Meetings of the Canadian Sociological Association, Ottawa, ON.
Session: Innovation in Social Research: New Data, New Questions, New
Analytics.

\ind May 2015 John McLevey, Amelia Howard, Alexander Graham, and Tiffany
Lin. ``Expertise, Stratification, and the Uncertain Democracy of Large
Free / Open Source Developer Communities.'' Presented at
\href{http://www.cf.ac.uk/socsi/contactsandpeople/harrycollins/expertise-project/seeshophome.html}{SEESHOP
9} (Studies of Expertise and Experience), Cardiff Wales, UK.

\ind August 2014 ``Think Tanks in the Space of Opinion: Tactics for
Creating Uncertainty about the Scientific Consensus on Climate Change.''
Presented at the Annual Meetings of the American Sociological
Association, San Francisco, CA.

\ind June 2014 ``Struggling Over Climate Expertise: `Consensus' and
`Skepticism' in the Space of Opinion.'' Presented at
\href{http://www.cf.ac.uk/socsi/contactsandpeople/harrycollins/expertise-project/seeshophome.html}{SEESHOP
8} (Studies of Expertise and Experience),
\emph{Communities of Integration}, Waterloo, ON, Canada.

\ind May 2014 Allyson Stokes and John McLevey. ``The Invisible Colleges
of Sociology in Canada: A Network Analysis, 1995-2014'' Annual meetings
of the Canadian Sociology Association, Brock University, St.~Catharines,
ON, Canada.

\ind May 2014 ``Funding, Fame, and Politics in the Think Tank World.''
Presented at \emph{The Science Policy Interface: International
Comparisons}, hosted by The Balsillie School of International Affairs,
Waterloo, ON, Canada.

\ind April 2014 Vanina Leschziner, Neil McLaughlin, and John McLevey
(equal authors). ``The American Fame Game: Public Renown and Academic
Status in the Social Sciences.'' Presented in \emph{Public Intellectuals
and Power}, Cambridge, MA. Harvard University.

\ind August 2014 ``Think Tanks in the Space of Opinion: Tactics for
Creating Uncertainty about the Scientific Consensus on Climate Change.''
Accepted for presentation at the Annual Meetings of the American
Sociological Association, San Francisco, CA.

\ind October 2013 Comments on papers in the session ``Chastened Dreams
and New Departures: American Scientific Culture(s) in Ferment from the
1960s to 1980s'' for the conference ``Total Money Makeover: Culture and
the Economization of Everything,'' organized by the Canadian Association
of American Studies (CAAS), University of Waterloo.

\ind August 2013 ``How do Think Tanks Produce and Promote Policy
Ideas?'' Presented in the ``Sociology of Knowledge'' regular session
(``Knowledge and the State''), Annual Meetings of the American
Sociological Association, New York, New York, US.

\ind June 2013 ``Think Tanks on Climate Change: Moral Views, Scientific
Credibility, and Political Contexts.'' Presented in ``The Sociology of
Climate Change,'' Annual meetings of the Canadian Sociology Association,
University of Victoria, Victoria, BC, Canada.

\ind June 2013 Vanina Leschziner, Neil McLaughlin, and John McLevey
(equal authors). ``The American Fame Game: Academic Status and Public
Renown in the Social Sciences.'' Presented in the ``The Role of Public
Intellectualism in Academe,'' Annual meetings of the Canadian Sociology
Association, University of Victoria, Victoria, BC, Canada.

\ind June 2012 ``Epistemic Cultures in the Production of Policy
Expertise'' Annual Qualitative Analysis Conference, Memorial University,
St John's NL, Canada.

\ind May 2012 ``Translation Work and the Marketing of Policy Expertise:
Leads from Research on Canadian Think Tanks.'' Annual meetings of the
Canadian Sociology Association, University of Waterloo and Wilfrid
Laurier University, Waterloo ON, Canada. Sociology of Science session.

\ind Aug 2011 ``Rhythms and Reason Giving: Understanding Academic
Involvement in Canadian Think Tanks.'' Annual meetings of the American
Sociology Association, Las Vegas, NV. Refinement of a paper presented in
Philadelphia earlier that year.

\ind April 2011 Invited participant in NYLON workshop ``Cultures of
Circulation.'' Ottawa ON, Canada.

\ind Feb 2011 (Previous version of) ``Rhythms and Reason Giving:
Understanding Academic Involvement in Canadian Think Tanks.'' Annual
meetings of the Eastern Sociology Society, Philadelphia PA, US. Regular
Session on ``Constructing Workplaces and Professional Domains.''

\ind May 2010 ``How and Why Do Academics Get Involved with Think
Tanks?'' Annual Qualitative Analysis Conference, Wilfrid Laurier
University, Brantford ON, Canada.

\ind June 2010 ``Contesting Education: A Comparative Frame Analysis of
Opinion Pieces by The Fraser Institute and The Canadian Centre for
Policy Alternatives.'' Annual meetings of the Canadian Sociology
Association, Concordia University, Montreal QC, Canada.

\ind June 2010 (with Lisa Kowalchuk and Neil McLaughlin) ``Public
Intellectual Work: Uses of the Canadian Op-Ed Column.'' Annual meetings
of the Canadian Sociology Association, Concordia University, Montreal
QC, Canada.

\ind May 2010 (Previous version of) ``Contesting Education: A
Comparative Frame Analysis of Opinion Pieces by The Fraser Institute and
The Canadian Centre for Policy Alternatives.'' Annual Qualitative
Analysis Conference, Wilfrid Laurier University, Brantford ON, Canada.

\ind May 2009 ``Understanding Marginality, Ambiguous Outcomes, and
Failure in Social Movements Research and the Sociology of Ideas.''
Annual meetings of the Canadian Sociology Association, Carleton
University, Ottawa ON, Canada.

\section{Invited Talks}\label{invited-talks}

\subsection{Invited Research Talks}\label{invited-research-talks}

\ind Nov 15, 2017 ``Gender discrimination in open source software
development: findings from a large-scale field study.'' Guest lecture in
Gender Equity course in Knowledge Integration, University of Waterloo.

\ind Nov 13, 2017. ``A Primer on Computational Sociology.'' Guest
lecture in Sociology Theory grad seminar, Sociology \& Legal Studies,
University of Waterloo.

\ind March 2, 2016 ``Network Structure and the `Chain of Trust' in Linux
Development: Lessons for Working with Data Scraped from the Web.'' Guest
lecture in Research Methods class in Sociology, Wilfrid Laurier
University

\ind May 2017, Panelist on ``SSHRC's new data management policies: what
do they mean for your knowledge making practices?'' at the 2017 Canadian
Sociological Association meetings, Ryerson University.

\ind Oct 28, 2016, ``Open Science and the Uncertain Future of
University-Industry Partnerships in Biomedical Research and
Development.'' Environment Seminar Series: Open Data, Open Science.
Faculty of Environment, University of Waterloo.

\ind Dec 2, 2014 ``Collaborating On-Line: An Analysis of Communication
Networks for Linux Kernel Developers.'' \href{http://wici.ca/}{Waterloo
Institute for Complexity and Innovation} Speaker Series, University of
Waterloo.

\ind Sept 20, 2013 ``Think Tanks, Funding, and Politics of Policy
Knowledge,'' Knowledge Integration Seminar Series, Faculty of
Environment, University of Waterloo.

\subsection{Invited Teaching Talks}\label{invited-teaching-talks}

\ind March 1, 2016 John McLevey and Patrick Famaran (UG student),
``Using Technology to Facilitate Collaboration,'' Centre for Teaching
Excellence Educational Technology Week.

\ind March 1, 2016 ``Enhancing Student Learning by Bringing Data into
the Classroom.'' GREEN TEA speaker series, University of Waterloo.

\section{Teaching}\label{teaching}

\subsection{Courses Designed, Developed, and Offered since
2013}\label{courses-designed-developed-and-offered-since-2013}

\noindent Research Methods (undergraduate lecture)\\
\noindent ``Big Data'' and Social Science Research (undergraduate
seminar)\\
\noindent KI Thesis / Senior Research Project\\
\noindent The Art \& Science of Learning (undergraduate lecture)\\
\noindent Data Visualization (undergraduate seminar)\\
\noindent Sociology of Science and Technology (undergraduate seminar)\\
\noindent Open Science and Technology (undergraduate seminar)\\
\noindent Creativity and Innovation (undergraduate lecture)

\subsection{Independent Studies
Courses}\label{independent-studies-courses}

\noindent Social Network Analysis (3x); Reproducibility and Replication
in the Sciences; Sociology of Science; Computational Sociology; The
Sociology of Expertise and Science Policy; Sociology of Organizations

\section{Student Supervision}\label{student-supervision}

\subsection{PhD Dissertations}\label{phd-dissertations}

\noindent Michael Clarke (committee member -- defended in 2016)\\
\noindent Alexander Graham (co-supervisor with Peter Carrington)\\
\noindent Amelia Howard (supervisor)\\
\noindent Tyler Crick (supervisor)\\
\noindent Julie Cook (co-supervisor with Jennifer Lynes)\\
\noindent Pierson Browne (committee member, supervisor Jen Whitson)\\
\noindent Rod Missaghian (committee member, supervisor Janice Aurini)\\
\noindent Yixi Yang (committee member, supervisor Mark Stoddart at
Memorial University)

\subsection{Master's Theses}\label{masters-theses}

\noindent Nicholas Brandon, MD (committee member, supervisor Shannon
Majowicz, defended 2018)\\
\noindent Alexander Graham (supervisor, defended 2017)\\
\noindent Junyi Wang (committee member, supervisor Derek Robinson,
defended in 2017)\\
\noindent Stuart Anderson (reader, supervisor Götz Hoeppe, defended
2017)\\
\noindent Chen Chen (reader, supervisor Peter Johnson, defended 2016)\\
\noindent Sarah Tang (committee member, supervisor Simron Singh)\\
\noindent Emerson LaCroix (committee member, supervisor Janice Aurini)

\subsection{Undergraduate Senior Honors
Theses}\label{undergraduate-senior-honors-theses}

\noindent Rachel Wood (completed 2018)\\
\noindent Jessilyn Wolfe (completed 2018)\\
\noindent Jillian Anderson (completed 2017)\\
\noindent Julia Yaroshinsky (completed 2016)\\
\noindent Tiffany Lin (completed 2015)\\
\noindent Benjamin Carr (completed 2014)\\
\noindent Chelsea Mills (completed 2014)\\
\noindent Christina Minji Chung (completed 2014)\\

\section{Other Teaching and Graduate Student
Mentoring}\label{other-teaching-and-graduate-student-mentoring}

\ind 2018-Present. Co-Instructor (with Eric Kennedy) for
\href{http://sotlnorth.ca}{Science Outside the Lab (SOtL) North}. A week
long intensive course in science policy held annually in Ottawa and
Montréal. Each course cohort is \textasciitilde{} 14 graduate students
from science and engineering disciplines across Canada.

\section{Service}\label{service}

\subsection{Service to the Profession}\label{service-to-the-profession}

\ind 2016-2020, Communications Officer, Member of the Executive Council,
Canadian Sociological Association. Am also managing social media
accounts for the \emph{Canadian Review of Sociology}.

\ind Co-organizer (with Rochelle Côté) and co-liaison with the Canadian
Sociological Association for the
\href{http://www.csa-scs.ca/files/webapps/csapress/socnet/}{Social
Networks Research Cluster}

\ind Co-organizer (with Marion Blute) and co-liaison with the Canadian
Sociological Association for the
\href{http://www.csa-scs.ca/files/webapps/csapress/sstk/}{Sociology of
Science, Technology, and Knowledge Research Cluster}

\ind Conference Session Organizing:\\
2017. \emph{Practical Advice on Communicating Sociological Research}
panel, Ryerson University\\
2017. \emph{Sociology of Science and Knowledge}, CSA Meetings, Ryerson
University\\
2016. \emph{Sociology of Science and Knowledge}, CSA Meetings,
University of Calgary\\
2015. \emph{Political Sociology of Science}, CSA Meetings, Carleton
University\\
2015. \emph{Sociology of Science}, CSA Meetings, Carleton University\\
2014. \emph{Sociology of Technology}, CSA meetings, Brock University\\
2014. \emph{Sociology of Culture}, with Allyson Stokes, CSA meetings,
Brock University

\ind Peer Reviewing (Journal Articles):\\
\emph{Science and Public Policy}\\
\emph{American Journal of Sociology}\\
\emph{Sociological Theory}\\
\emph{Social Studies of Science}\\
\emph{Canadian Journal of Sociology}\\
\emph{Methodological Innovations}\\
\emph{Acta Sociologica}

\ind Peer Reviewing (Grants):\\
2017. Observer for the 2018 SSHRC Postdoctoral Awards Competition\\
2017. Evaluator for 2017 SSHRC Insight Development Grants Competition

\subsection{University of Waterloo}\label{university-of-waterloo}



\item 2016 Internal External Examiner for PhD Dissertation in the Department of Applied Mathematics, University of Waterloo. John Lang, ``Mathematical Modelling of Social Factors in Decision Making Processes at the Individual and Population Levels.'' Dissertation Supervisors: Drs. Hans De Sterck and Daniel M. Abrams.

\item 2016 Internal External Examiner for PhD Dissertation in the Department of Philosophy, University of Waterloo. Benjamin Nelson, ``The Depictions of Unwritten Law.'' Committee Members: Brian Orend, Heather Douglas, and Matt Doucet.


\item 2016 Co-organized (with Ian Milligan) a \href{http://software-carpentry.org/}{Software Carpentry} workshop at the University of Waterloo focusing on shell scripting, git, and Python for social scientific and historical research.

\item 2016-Present Faculty Advisor, \href{http://2015.igem.org/Team:Waterloo}{University of Waterloo iGEM} (International Genetically Engineered Machine) Team, Policy \& Practices Subgroup, Mathematical Modeling Subgroup (occasionally). 2016 Gold Medal Winners.

\item 2014 Internal External Examiner for PhD Dissertation in the Department of Psychology, University of Waterloo. Nathaniel Barr, ``Reasoned connections: Complex creativity and dual-process theories of cognition.'' Dissertation Advisor: Jonathon Fugelsang.




\ind 2014 Gave a talk on creativity and innovation to Grade 11 students
at Waterloo Unlimited. Title: ``Where do good ideas come from? A social
network perspective.''\\




\subsection{McMaster University}\label{mcmaster-university}

\ind 2011--2012 Selection Committee member for two tenure-track hires in
Sociology\\
\ind 2010--2012 Chair of Graduate Student Caucus\\
\ind 2011--2012 PhD (ABD) Representative on the Graduate Committee\\
\ind 2009--2010 PhD Representative on the Graduate Committee\\
\ind 2009--2010 Co-Organizer, Culture and Politics workshop\\
\ind 2009--2012 Co-Organizer of Jane Synge Memorial Conferences\\
\ind 2009--2012 Peer Mentor in Sociology Peer Mentoring Program\\
\ind 2008--2009 Union Steward, Sociology (CUPE 3906)

\section{Additional Research Methods / Technical
Training}\label{additional-research-methods-technical-training}

\ind Technical / methods workshops attended at Sunbelt 2016, Newport
Beach, USA: (1) Understanding Diffusion with netdiffuseR, (2) Moving
beyond Descriptives: Basic Network Statistics with statnet, (3)
Exponential Family Random Graph Modeling (ERGMs) Using statnet, (4)
Introduction to Egocentric Network Data Analysis with ERGMs and TERGMs
Using statnet

\ind Technical / methods workshops attended at Sunbelt 2015, Brighton,
UK: (1) Networks in Python: The \emph{networkx} Package, Parts 1 \& 2,
(2) Mining of large social networks from Twitter, Facebook and LinkedIn
using Python, (3) Social Network Approaches for Behavior Change, (4)
Visualizing Social Networks. How to Create Meaningful and Compelling
Network Drawings.

\ind Qualitative Comparative Analysis and Fuzzy Sets. Arizona Methods
Workshops, held at University of Arizona. January, 2012.

\ind Hierarchical Linear Models. Inter-University Consortium for
Political and Social Research (ICPSR), held at University of
Massachusetts, Amherst. June, 2011.

\section{Research and Teaching
Assistantships}\label{research-and-teaching-assistantships}

\ind 2010--2013 \emph{Research Assistant} for Neil McLaughlin,
Sociology, McMaster University. ``Shaping Opinion in the Public Sphere:
Public Intellectual Authority in the Journalistic Field.'' Funded by
SSHRC Standard Research Grant.

\ind 2009--2010 \emph{Teaching Assistant} for Classical and Contemporary
Sociological Theory. Neil McLaughlin, Sociology, McMaster University.

\ind 2008--2009 \emph{Research Assistant} for Neil McLaughlin,
Sociology, McMaster University. ``Professors as Public Intellectuals.''
Funded by SSHRC Standard Research Grant.

\section{Professional Memberships}\label{professional-memberships}

\noindent Canadian Sociological Association, American Sociological
Association, International Network for Social Network Analysis, Society
for Social Studies of Science, Sociologists for Women in Society

\section{References}\label{references}

\ind Harry Collins, Fellow of the British Academy, Distinguished
Research Professor, School of Social Sciences, Cardiff University,
\href{mailto:CollinsHM@cf.ac.uk}{\nolinkurl{CollinsHM@cf.ac.uk}}

\ind Mike Gorman, Director and Professor of Science, Technology \&
Society Program, Professor of Systems Engineering, School of Engineering
and Applied Science, University of Virginia,
\href{mailto:meg3c@virginia.edu}{\nolinkurl{meg3c@virginia.edu}}

\ind Marion Blute, Professor Emeritus, Department of Sociology,
University of Toronto,
\href{mailto:marion.blute@utoronto.ca}{\nolinkurl{marion.blute@utoronto.ca}}

\ind Howard Ramos, Professor; Associate Dean Research, Faculty of Arts
and Social Sciences, Department of Sociology \& Anthropology, Dalhousie
University,
\href{mailto:howard.ramos@dal.ca}{\nolinkurl{howard.ramos@dal.ca}}

\ind Neil McLaughlin, Professor, Sociology, McMaster University,
\href{mailto:nmclaugh@mcmaster.ca}{\nolinkurl{nmclaugh@mcmaster.ca}}

\ind Tina Fetner, Associate Professor, Sociology, McMaster University,
\href{mailto:tina.fetner@mcmaster.ca}{\nolinkurl{tina.fetner@mcmaster.ca}}

\ind Scott Davies, Professor, Leadership, Higher and Adult Education,
University of Toronto, OISE,
\href{mailto:scott.davies@utoronto.ca}{\nolinkurl{scott.davies@utoronto.ca}}
