%!TEX program = xelatex
\documentclass[9pt,usenames,dvipsnames]{article}

%%%------------------------------------------------------------------------
%%% Metadata
%%%------------------------------------------------------------------------

\def\myauthor{JOHN MCLEVEY}
\def\mytitle{Vita}
\def\mycopyright{\myauthor}
\def\mykeywords{}
\def\mybibliostyle{plain}
\def\mybibliocommand{}
\def\mysubtitle{}
\def\myaffiliation{University of Waterloo}
\def\myaddress{Department of Knowledge Integration, Faculty of Environment \\ Sociology and Legal Studies, Environment and Resource Studies}
\def\myemail{john.mclevey@uwaterloo.ca}
\def\myweb{www.johnmclevey.com}
\def\myphone{(647) 921-2044}
\def\myversion{}
\def\myrevision{}

\def\myaffiliation{University of Waterloo}
\def\myauthor{JOHN MCLEVEY}
\date{}
\def\mykeywords{John, McLevey, John McLevey, Vita, CV, Resume, Sociology}

% \immediate\write18{sh ./vc}
% \input{vc.tex}

%%%------------------------------------------------------------------------
%%% Required style files
%%%------------------------------------------------------------------------
\usepackage{url,fancyhdr}
\usepackage[none]{hyphenat} % remove hyphenation
\usepackage{fontawesome}

%% needed for xelatex to work
\usepackage{fontspec}
\usepackage{xunicode}

%% color for the links 
\usepackage[usenames,dvipsnames]{color}

%% hyperlinks
\usepackage[xetex, 
	colorlinks=true,
	urlcolor=BlueViolet,
	plainpages=false,
  	pdfpagelabels,
  	bookmarksnumbered,
  	pdftitle={\mytitle},
  	pagebackref,
  	pdfauthor={\myauthor},
  	pdfkeywords={\mykeywords}
  	]{hyperref}

%%%------------------------------------------------------------------------
%%% Document
%%%------------------------------------------------------------------------
\begin{document}

\setromanfont[Mapping={tex-text},Numbers={OldStyle},Ligatures={Common}]{Crimson Text Regular} 
\setsansfont[Mapping=tex-text]{Lato Semibold}
\setmonofont[Mapping=tex-text,Scale=0.9]{Inconsolata} 
\newfontfamily\myfont[Mapping=tex-text]{Lato Black}

\setkeys{Gin}{width=1\textwidth} 

%%%------------------------------------------------------------------------
%%% Local commands
%%%------------------------------------------------------------------------

%% Marginal header
%% Note: as the document goes on you may need to introduce a (gradually increasing)
%% \vspace element to keep the marginal header pleasingly aligned with the first 
%% item in the body text. Like this: \marginhead{{\vskip 0.4em}Grants}, or 
%% \marginhead{{\vskip 0.8em}Service}. Experiment as needed.
\newcommand{\marginhead}[1]{\marginpar{\textsf{{\footnotesize\vspace{-1em}\flushright #1}}}}

%% custom ampersand (font consistent with the one chosen above)
\newcommand{\amper}{{\fontspec[Scale=.95,Colour=AA0000]{Minion Pro Medium}\selectfont\&\,}}

%% No bullets on labels
\renewcommand{\labelitemi}{~} 

%% Custom hanging indent for vita items
\def\ind{\hangindent=1 true cm\hangafter=1 \noindent}
%\def\ind{\hangindent=18pt\hangafter=1 \noindent}
\def\labelitemi{~}
\renewcommand{\labelitemii}{~}

%%%------------------------------------------------------------------------
%%% Page layout
%%%------------------------------------------------------------------------
\pagestyle{fancy}
\renewcommand{\headrulewidth}{0pt}
\fancyhead{}
\fancyfoot{}
\rhead{{\scriptsize\thepage}}

%% git revision control footer 
% \rfoot{\texttt{\scriptsize \VCRevision\ on \VCDateTEX}} % git revision info inserted via external script -- see docs for vc package for details. comment out this line if you're not using vc, and also remove the \input{vc} line above.

%%%------------------------------------------------------------------------
%%% Address and contact block
%%%------------------------------------------------------------------------
%% Name 
% \noindent{\huge {\textsc{john mclevey}}}
% \reversemarginpar

\begin{minipage}[t]{2.95in}
 \flushright \footnotesize \href{https://uwaterloo.ca/}{University of Waterloo} \\  \href{https://uwaterloo.ca/knowledge-integration/faculty-mclevey}{Department of Knowledge Integration} \\ Waterloo, ON, Canada, N2L 3G1\\
  \end{minipage}
\hfill     
\hfill
\begin{minipage}[t]{1.7in}
  \flushright \footnotesize \myphone\, \faPhone \\
  {\texttt{\href{mailto:\myemail}{\myemail}} \, \faEnvelope} \\
  {\texttt{\href{\myweb}{\myweb}} \, \faGlobe} \\
\end{minipage}


\bigskip

%% Name 
\noindent{\large {\myfont John McLevey}} \\
\noindent{\emph{Short CV}}
\reversemarginpar

\bigskip 
\marginhead{APPOINTMENTS}
\smallskip 
\noindent 2013-present. Assistant Professor (tenure track), University of Waterloo \\
\noindent Department of Knowledge Integration, Faculty of Environment \\
\noindent Department of Sociology and Legal Studies, Faculty of Arts \\
\noindent Environment and Resource Studies, Faculty of Environment \\
\smallskip

\marginhead{AFFILIATIONS}

\ind 2014-present. Affiliate Researcher, \href{http://wici.ca/new/}{Waterloo Institute for Complexity and Innovation}, University of Waterloo

\ind 2014-present. Fellow, Science and Health Policy Research Cluster, \href{http://www.balsillieschool.ca/}{Balsillie School of International Affairs}, University of Waterloo \\

\medskip 
\marginhead{EDUCATION}

\noindent 2013. PhD, Sociology, McMaster University \\
\noindent 2009. MA, Sociology, McMaster University \\
\noindent 2008. BA Honors, Sociology, Memorial University \\

\marginhead{RESEARCH AREAS}

\noindent Sociology of Science and Expertise; Social Networks; Knowledge Diffusion; Environmental Sociology \\

\marginhead{PUBLICATIONS}

\ind \textbf{Peer Reviewed Journal Articles} \\

\ind John McLevey. 2015. ``Understanding Policy Research in Liminal Spaces: Think Tank Responses to Diverging Principles of Legitimacy.'' In Press at \emph{Social Studies of Science}. \\

\ind John McLevey. 2014. ``Think Tanks, Funding, and the Politics of Policy Knowledge in Canada.'' \emph{Canadian Review of Sociology / Revue canadienne de sociologie}. 51(1):54-75.\\

\marginhead{SELECTED CONFERENCES SINCE 2010}

\noindent American Sociological Association (5 presentations, full papers), Canadian Sociological Association (6 presentations), Eastern Sociological Association (1 presentation), Science Policy Interface in Canada, the US, and UK (1 presentation), Communities of Integration: Studies of Expertise and Experience (1 presentation), Public Intellectuals (1 presentation)\\

\marginhead{SELECTED GRANTS, AWARDS}

\ind 2014-2016 \href{http://www.sshrc-crsh.gc.ca/funding-financement/programs-programmes/insight_development_grants-su
bventions_de_developpement_savoir-eng.aspx}{Social Science and Humanities Research Council of Canada (\textbf{SSHRC}), Insight Development Grant}, John McLevey, ``Collaborative Design in Online Networks,'' \$74,814. \\

\ind 2010–2013 \href{http://www.sshrc-crsh.gc.ca/funding-financement/programs-programmes/fellowships/doctoral-doctorat-eng.aspx}{Joseph-Armand Bombardier Canada Graduate Scholarship}, Category A, SSHRC Doctoral Scholarship, \$105,000. \\

\ind 2009–2013 PhD Graduate Scholarship, McMaster University, \$52,000. Declined. (\$10,000 replaced by Ontario Graduate Fellowship in 2009–2010, replaced by SSHRC CGS 2010–2013) \\

\ind 2010–2011 Ontario Graduate Scholarship, \$15,000. Declined. \\

\ind 2009–2010 Ontario Graduate Fellowship, \$12,000. Sociology Department Top Up, \$3,000. \\

\noindent \emph{Grant Applications Under Review}: Co-Applicant or Partner on 3 grant applications currently under review \\ 
% with Katie P, Mark S, Vanessa S, and the Internet of Things grant

\marginhead{TRAINING HIGHLY QUALIFIED PERSONNEL}

\ind \emph{Research Assistants Supervised}: Evaleen Hellinga (2013-14), Alexander Graham (2013-present), Amelia Howard (2013-present), Tiffany Lin (2014-present) 

\ind \emph{Dissertation Co-Supervision and Committees}: Amelia Howard (co-supervisor), Noorin Manji (committee member), Michael Clarke (committee member)

\ind \emph{Senior Honors Theses Supervision}: Tiffany Lin (in progress, Benjamin Carr (in progress), Chelsea Mills (completed 2014), Christina Minji Chung (completed 2014) \\

\marginhead{SERVICE}

\ind \textbf{Service to the Profession}

\ind Peer Reviewing: {\it Sociological Theory}, {\it Canadian Journal of Sociology}

\ind Co-organizer (with Marion Blute) and co-liaison (with Daphné Esquivel Sada) with the Canadian Sociological Association for the \href{http://www.csa-scs.ca/files/webapps/csapress/sstk/}{Sociology of Science, Technology, and Knowledge Research Cluster}

\ind Session Organizing: Political Sociology of Science (CSA Meetings, 2015, Carleton University), Sociology of Science (CSA Meetings, 2015, Carleton University), Sociology of Technology (CSA meetings, 2014, Brock University), Sociology of Culture (CSA meetings, 2014, Brock University) \\

%% Additional Training
\marginhead{ADDITIONAL RESEARCH METHODS TRAINING}

\ind Qualitative Comparative Analysis and Fuzzy Sets. Arizona Methods Workshops, held at University of Arizona. January, 2012.

\ind Hierarchical Linear Models. Inter-University Consortium for Political and Social Research (ICPSR), held at University of Massachusetts, Amherst. June, 2011.\\

\end{document}