%!TEX program = xelatex
\documentclass[9pt,usenames,dvipsnames]{article}

%%%------------------------------------------------------------------------
%%% Metadata
%%%------------------------------------------------------------------------

\def\myauthor{JOHN MCLEVEY}
\def\mytitle{Vita}
\def\mycopyright{\myauthor}
\def\mykeywords{}
\def\mybibliostyle{plain}
\def\mybibliocommand{}
\def\mysubtitle{}
\def\myaffiliation{University of Waterloo}
\def\myaddress{Department of Knowledge Integration, Faculty of Environment \\ Sociology and Legal Studies, Environment and Resource Studies}
\def\myemail{john.mclevey@uwaterloo.ca}
\def\myweb{www.johnmclevey.com}
\def\myphone{(647) 921-2044}
\def\myversion{}
\def\myrevision{}
\def\lastupdated{Last Updated: July 1, 2015} 

\def\myaffiliation{University of Waterloo}
\def\myauthor{JOHN MCLEVEY}
\date{}
\def\mykeywords{John, McLevey, John McLevey, Vita, CV, Resume, Sociology}

% \immediate\write18{sh ./vc}
% \input{vc.tex}

%%%------------------------------------------------------------------------
%%% Required style files
%%%------------------------------------------------------------------------
\usepackage{url,fancyhdr}
\usepackage[none]{hyphenat} % remove hyphenation
\usepackage{fontawesome}

%% needed for xelatex to work
\usepackage{fontspec}
\usepackage{xunicode}

%% color for the links 
\usepackage[usenames,dvipsnames]{color}

%% hyperlinks
\usepackage[xetex, 
  colorlinks=true,
  urlcolor=BlueViolet,
  plainpages=false,
    pdfpagelabels,
    bookmarksnumbered,
    pdftitle={\mytitle},
    pagebackref,
    pdfauthor={\myauthor},
    pdfkeywords={\mykeywords}
    ]{hyperref}

%%%------------------------------------------------------------------------
%%% Document
%%%------------------------------------------------------------------------
\begin{document}

% \setromanfont[Mapping={tex-text},Numbers={OldStyle},Ligatures={Common}]{Crimson Text Regular} 
\setromanfont[Mapping={tex-text},Numbers={OldStyle},Ligatures={Common}]{Minion Pro} 
\setsansfont[Mapping=tex-text]{Minion Pro}
\setmonofont[Mapping=tex-text,Scale=0.9]{Inconsolata} 
\newfontfamily\myfont[Mapping=tex-text]{Minion Pro}

\setkeys{Gin}{width=1\textwidth} 

%%%------------------------------------------------------------------------
%%% Local commands
%%%------------------------------------------------------------------------

%% Marginal header
%% Note: as the document goes on you may need to introduce a (gradually increasing)
%% \vspace element to keep the marginal header pleasingly aligned with the first 
%% item in the body text. Like this: \section*{{\vskip 0.4em}Grants}, or 
%% \section*{{\vskip 0.8em}Service}. Experiment as needed.
\newcommand{\marginhead}[1]{\marginpar{\textsf{{\footnotesize\vspace{-1em}\flushright #1}}}}

%% custom ampersand (font consistent with the one chosen above)
\newcommand{\amper}{{\fontspec[Scale=.95,Colour=AA0000]{Minion Pro Medium}\selectfont\&\,}}

%% No bullets on labels
\renewcommand{\labelitemi}{~} 

%% Custom hanging indent for vita items
\def\ind{\hangindent=1 true cm\hangafter=1 \noindent}
%\def\ind{\hangindent=18pt\hangafter=1 \noindent}
\def\labelitemi{~}
\renewcommand{\labelitemii}{~}

%%%------------------------------------------------------------------------
%%% Page layout
%%%------------------------------------------------------------------------
\pagestyle{fancy}
\renewcommand{\headrulewidth}{0pt}
\fancyhead{}
\fancyfoot{}
\rhead{{\scriptsize\thepage}}

\begin{minipage}[t]{2.95in}
 \flushright \footnotesize \href{https://uwaterloo.ca/}{University of Waterloo} \\  \href{https://uwaterloo.ca/knowledge-integration/faculty-mclevey}{Department of Knowledge Integration} \\ Waterloo, ON, Canada \\ N2L 3G1\\
  \end{minipage}
\hfill     
\hfill
\begin{minipage}[t]{1.7in}
  \flushright \footnotesize \myphone\, \faPhone \\
  {\texttt{\href{mailto:\myemail}{\myemail}} \, \faEnvelope} \\
  {\texttt{\href{\myweb}{\myweb}} \, \faGlobe} \\
  {\texttt{\lastupdated}}\\
\end{minipage}

\bigskip

\section*{A) PERSONAL DATA}

\subsection*{1. Name}

John Vincent Patrick McLevey

\subsection*{2. Position}

Assistant Professor, Tenure-Track 

\subsection*{3. Department}

\noindent Department of Knowledge Integration, Faculty of Environment \\   
\noindent Cross-Appointed to Sociology \& Legal Studies, Faculty of Arts \\ 
\noindent Cross-Appointed to Environment \& Resource Studies, Faculty of Environment \\

\noindent \emph{Affiliations}\\

\noindent 2014-present Affiliate Researcher, Waterloo Institute for Complexity and Innovation, University of Waterloo \\

\noindent 2014-present Fellow, Balsillie School of International Affairs, Science and Health Policy Research Cluster

\subsection*{4. Degrees}

\noindent PhD, Sociology, McMaster University, June 24 2013 \\  
\noindent MA, Sociology, McMaster University, 2009  \\
\noindent BA Honors, Sociology, Memorial University of Newfoundland, 2008

\subsection*{5. Awards \& Honours}

See section on research funding

\subsection*{6. Relevant Professional Employment}

\noindent 2013-present Assistant Professor, University of Waterloo \\   

\noindent 2010-2013 Research Assistant for Neil McLaughlin, Sociology, McMaster University. ``Shaping Opinion in the Public Sphere: Public Intellectual Authority in the Journalistic Field.'' Funded by SSHRC Standard Research Grant. \\

\noindent 2009-2010 Teaching Assistant for Classical and Contemporary Sociological Theory, Sociology, McMaster University. \\

\noindent 2008-2009 Research Assistant for Neil McLaughlin, Sociology, McMaster University. ``Professors as Public Intellectuals.'' Funded by SSHRC Standard Research Grant.

\section*{B) RESEARCH \& SCHOLARSHIP}

\subsection*{1. Areas of Interest}

Social Networks, Sociology of Knowledge, Expertise and Governance, Environmental Sociology, Social Movements / Collective Action, Sociology of Culture

\subsection*{2. Publications}

\begin{table}[h!]
\caption{Summary of Publications}\centering
\begin{tabular}{lcc} 
\hline                          
 & Number \\ 
\hline 
Articles in Peer Reviewed Journals & 2 \\
Articles Under Review at Peer Reviewed Journals & 4 \\
Articles in Preparation for Submission & 3 \\
Op-Eds & 1 \\
\hline
\end{tabular}
\end{table}

\subsubsection*{Articles in Refereed Journals}

\ind John McLevey. 2015. ``Understanding Policy Research in Liminal Spaces: Think Tank Responses to Diverging Principles of Legitimacy.'' \emph{Social Studies of Science}. 45(2):270-293. \\

\ind John McLevey. 2014. ``Think Tanks, Funding, and the Politics of Policy Knowledge in Canada.'' \emph{Canadian Review of Sociology / Revue canadienne de sociologie}. 51(1):54-75.

\subsubsection*{Articles in Refereed Conference Proceedings}

\subsubsection*{Chapters in Books}

\subsubsection*{Books}

\subsubsection*{Op-Eds}

\ind ``\href{http://bit.ly/1ohSn1N}{Tory war on evidence claims another casualty}'' with Liam Swiss. \emph{Toronto Star} Op-Ed published on September 24 2014, section A15. 

\subsubsection*{Manuscripts Submitted for Publication}

\ind Allyson Stokes and John McLevey (equal authors). ``From Porter to Bourdieu: The Evolving Specialty Structure of Canadian Sociology in Comparative Perspective, 1966- 2014'' \emph{Under Review} \\

\ind Vanina Leschziner, Neil McLaughlin, and John McLevey (equal authors). ``The American Fame Game: Academic Status and Public Renown in the Social Sciences.'' \emph{Under Review} \\ 

\ind John McLevey. ``The Structure of an Open Source Collaboration Network: An Analysis of Linux Kernel Development.'' \emph{Under Review} \\ % to American Sociological Review

\ind John McLevey. ``Climate Change and Strange Transmuted Expertise.'' \emph{Under Review} % to Environmental Politics

\subsection*{3. Innovative Designs}

NA

\subsection*{4. Presentations at Scholarly Conferences}

\begin{table}[h!]
\caption{Summary of Conference Presentations since 2009}\centering
\begin{tabular}{lcc} 
\hline                          
Conference & No. of Papers \\ 
\hline 
Canadian Sociological Association & 8 \\
American Sociological Association & 4 \\
Eastern Sociological Society & 1 \\
Sunbelt / International Network for Social Network Analysis & 1 \\
American Society of Criminology & 1 \\
Specialty Conferences & 9 \\
\hline
\end{tabular}
\end{table}

\smallskip

\ind November 2015 Owen Gallupe, Sarah Brown, and John McLevey. ``Selection or influence? A meta-analysis of the association between peer and personal offending.'' Accepted for presentation at the Annual Meeting of the American Society of Criminology, Washington, D.C.\\

\ind August 2015 ``Conflict and Cooperation in Large Collaboration Networks: An Analysis of Linux Kernel Development.'' Accepted for Presentation at the Annual Meetings of the American Sociological Association, Chicago, IL. Session: Sociology of Technology. \\

\ind June 2015 ``Conflict and Cooperation in Large Collaboration Networks: An Analysis of Linux Kernel Development.'' Presented at Sunbelt meetings, International Network for Social Network Analysis (INSNA), Brighton, UK. \\

\ind May 2015 ``Conflict and Cooperation in Large Collaboration Networks: An Analysis of Linux Kernel Development.'' Presented at the Annual Meetings of the Canadian Sociological Association, Ottawa, ON. Session: Innovation in Social Research: New Data, New Questions, New Analytics.\\

\ind May 2015 John McLevey, Amelia Howard, Alexander Graham, and Tiffany Lin. ``Expertise, Stratification, and the Uncertain Democracy of Large Free / Open Source Developer Communities.'' Presented at \href{http://www.cf.ac.uk/socsi/contactsandpeople/harrycollins/expertise-project/seeshophome.html}{SEESHOP 9} (Studies of Expertise and Experience), Cardiff Wales, UK. \\

\ind August 2014 ``Think Tanks in the Space of Opinion: Tactics for Creating Uncertainty about the Scientific Consensus on Climate Change.'' Presented at the Annual Meetings of the American Sociological Association, San Francisco, CA. \\

\ind June 2014 ``Struggling Over Climate Expertise: `Consensus' and `Skepticism' in the Space of Opinion.'' Presented at \href{http://www.cf.ac.uk/socsi/contactsandpeople/harrycollins/expertise-project/seeshophome.html}{SEESHOP 8} (Studies of Expertise and Experience), \emph{Communities of Integration}, Waterloo, ON, Canada. \\

\ind May 2014 Allyson Stokes and John McLevey. ``The Invisible Colleges of Sociology in Canada: A Network Analysis, 1995-2014'' Annual meetings of the Canadian Sociology Association, Brock University, St. Catharines, ON, Canada.\\

\ind May 2014 ``Funding, Fame, and Politics in the Think Tank World.'' Presented at \emph{The Science Policy Interface: International Comparisons}, hosted by The Balsillie School of International Affairs, Waterloo, ON, Canada. \\

\ind April 2014 Vanina Leschziner, Neil McLaughlin, and John McLevey (equal authors). ``The American Fame Game: Public Renown and Academic Status in the Social Sciences.'' Presented in \emph{Public Intellectuals and Power}, Cambridge, MA. Harvard University. \\

\ind August 2014 ``Think Tanks in the Space of Opinion: Tactics for Creating Uncertainty about the Scientific Consensus on Climate Change.'' Accepted for presentation at the Annual Meetings of the American Sociological Association, San Francisco, CA. \\

\ind October 2013 Comments on papers in the session ``Chastened Dreams and New Departures: American Scientific Culture(s) in Ferment from the 1960s to 1980s'' for the conference ``Total Money Makeover: Culture and the Economization of Everything,'' organized by the Canadian Association of American Studies (CAAS), University of Waterloo. \\

\ind August 2013 ``How do Think Tanks Produce and Promote Policy Ideas?'' Presented in the ``Sociology of Knowledge'' regular session (``Knowledge and the State''), Annual Meetings of the American Sociological Association, New York, New York, US. \\

\ind June 2013 ``Think Tanks on Climate Change: Moral Views, Scientific Credibility, and Political Contexts.'' Presented in ``The Sociology of Climate Change,'' Annual meetings of the Canadian Sociology Association, University of Victoria, Victoria, BC, Canada. \\

\ind June 2013 Vanina Leschziner, Neil McLaughlin, and John McLevey (equal authors). ``The American Fame Game: Academic Status and Public Renown in the Social Sciences.'' Presented in the ``The Role of Public Intellectualism in Academe,'' Annual meetings of the Canadian Sociology Association, University of Victoria, Victoria, BC, Canada. \\

\ind June 2012 ``Epistemic Cultures in the Production of Policy Expertise'' Annual Qualitative Analysis Conference, Memorial University, St John's NL, Canada.\\

\ind May 2012 ``Translation Work and the Marketing of Policy Expertise: Leads from Research on Canadian Think Tanks.'' Annual meetings of the Canadian Sociology Association, University of Waterloo and Wildrid Laurier University, Waterloo ON, Canada. Sociology of Science session.\\

\ind Aug 2011 ``Rhythms and Reason Giving: Understanding Academic Involvement in Canadian Think Tanks.'' Annual meetings of the American Sociology Association, Las Vegas, NV. Refinement of a paper presented in Philadelphia earlier that year. \\

\ind April 2011 Invited participant in NYLON workshop ``Cultures of Circulation.'' Ottawa ON, Canada.\\

\ind Feb 2011 (Previous version of) ``Rhythms and Reason Giving: Understanding Academic Involvement in Canadian Think Tanks.'' Annual meetings of the Eastern Sociology Society, Philadelphia PA, US. Regular Session on ``Constructing Workplaces and Professional Domains.''\\

\ind May 2010 ``How and Why Do Academics Get Involved with Think Tanks?'' Annual Qualitative Analysis Conference, Wilfrid Laurier University, Brantford ON, Canada.\\

\ind June 2010 ``Contesting Education: A Comparative Frame Analysis of Opinion Pieces by The Fraser Institute and The Canadian Centre for Policy Alternatives.'' Annual meetings  of the Canadian Sociology Association, Concordia University, Montreal QC, Canada.\\

\ind June 2010 (with Lisa Kowalchuk and Neil McLaughlin) ``Public Intellectual Work: Uses of the Canadian Op-Ed Column.'' Annual meetings of the Canadian Sociology Association, Concordia University, Montreal QC, Canada.\\

\ind May 2010 (Previous version of) ``Contesting Education: A Comparative Frame Analysis of Opinion Pieces by The Fraser Institute and The Canadian Centre for Policy Alternatives.'' Annual Qualitative Analysis Conference, Wilfrid Laurier University, Brantford ON, Canada.\\

\ind May 2009 ``Understanding Marginality, Ambiguous Outcomes, and Failure in Social Movements Research and the Sociology of Ideas.'' Annual meetings of the Canadian Sociology Association, Carleton University, Ottawa ON, Canada.\\

\subsection*{5. Record of Research Applications}

\begin{table}[h!]
\caption{Summary of Research Funding Applications since 2013}\centering
\begin{tabular}{lcr} 
\hline                          
 & No. of Applications & Amount \\ 
\hline 
Total Received as PI & 1 & \$74,814.00\\
Total Received as Co-I & 1 & \$188,423.00\\
Total Applications Currently Being Considered & 2 & \$13,165.20\\
Funding Applications in Progress  & 2 & \$225,000.00 \\
Non-Competitive Funding &  & \$15,000.00 \\
\hline
\end{tabular}
\end{table}
\smallskip

\subsubsection*{Funded Applications}

\ind 2015-2020 Co-Investigator, \href{http://www.sshrc-crsh.gc.ca/funding-financement/programs-programmes/insight_development_grants-su
bventions_de_developpement_savoir-eng.aspx}{Social Science and Humanities Research Council of Canada (\textbf{SSHRC})}, Insight Grant, ``The Oil-Tourism Interface and Social-Ecological Change in the North Atlantic,'' Principal Investigator: Dr. Mark Stoddart, Department of Sociology, Memorial University, \$188,423. \\

\ind 2014-2016 Principal Investigator, \href{http://www.sshrc-crsh.gc.ca/funding-financement/programs-programmes/insight_development_grants-su
bventions_de_developpement_savoir-eng.aspx}{Social Science and Humanities Research Council of Canada (\textbf{SSHRC}), Insight Development Grant}, John McLevey, ``Collaborative Design in Online Networks,'' \$74,814.

\subsubsection*{Total Applications Currently Being Considered}

\ind John McLevey (PI), LITE Seed Grant, Center for Teaching Excellence, University of Waterloo, ``A Data-Driven and Interactive Approach to Enhancing Student Learning about Disciplinary and Interdisciplinary Knowledge Production,'' Requested: \$4,765.20. \\

\ind John McLevey (PI) and Vanessa Schweizer (Co-I), Basillie School of International Affairs, Major Workshops Grant, ``Challenges and Opportunities for Governance of Socio-Ecological Systems in Comparative Perspective,'' Requested: \$8,400.  

\subsubsection*{Funding Applications in Progress}

\ind John McLevey (PI), Ontario Early Researcher Award, Ministry of Research and Innovation, ``Collaborative Design in Large Online Networks,'' Requested: \$150,000. \\

\ind Owen Gallup (PI) and John McLevey (Co-I), Social Science and Humanities Research Council of Canada, Insight Development Grant, Requested: \$75,000.

\subsubsection*{Unsuccessful Funding Applications}

\ind Katie Plaisance (PI) and John McLevey (Co-I), Social Science and Humanities Research Council of Canada (SSHRC), Insight Development Grant, ``Mapping the Uptake of Philosophy of Science in the Sciences,'' Requested: \$74,120. 

\subsubsection*{Non-Competitive Funding}

\ind 2013 University of Waterloo, Faculty Research Startup Grant, \$15,000.   

\subsubsection*{Competitive Funding During PhD}

\ind 2010–2013 \href{http://www.sshrc-crsh.gc.ca/funding-financement/programs-programmes/fellowships/doctoral-doctorat-eng.aspx}{Joseph-Armand Bombardier Canada Graduate Scholarship}, Category A, SSHRC Doctoral Scholarship, \$105,000.\\

\ind 2010–2011 Ontario Graduate Scholarship, \$15,000. Declined.\\

\ind 2009–2010 Ontario Graduate Fellowship, \$12,000. Sociology Department Top Up, \$3,000.\\

\section*{C) SERVICE} 

\subsection*{1. Committees}

\subsubsection*{University}

\noindent 2014 Board Member, \href{http://math.uwaterloo.ca/survey-research-centre/node/1}{University of Waterloo Survey Research Centre} 

\subsubsection*{Faculty}

\ind 2014-2015 Faculty of Environment representative on the Arts Faculty Council, University of Waterloo \\

\ind 2014-2015 Department of Knowledge Integration representative on the Environment Faculty Council, University of Waterloo \\

\ind 2014 University of Waterloo, Faculty of Environment Teaching and Learning Committee

\subsubsection*{Department / School}

\ind 2015-present Knowledge Integration Learning Outcomes Committee \\

\ind 2014-present Knowledge Integration Seven Year Review Committee 

\subsubsection*{2. Other University Service}

\subsubsection*{3. Community Service Relevant to Professional Expertise}

\ind March 10 2014, gave a talk on creativity and innovation to Grade 11 students at Waterloo Unlimited. Title: ``Where do good ideas come from? A social network perspective.''

\section*{D) PROFESSIONAL ACTIVITIES} 

\subsection*{1. Positions Held or Service to Professional Societies}

\noindent Co-organizer (with Marion Blute) and co-liaison (with Daphné Esquivel Sada) with the Canadian Sociological Association for the \href{http://www.csa-scs.ca/files/webapps/csapress/sstk/}{Sociology of Science, Technology, and Knowledge Research Cluster}\\

\noindent Session Organizing: Political Sociology of Science (CSA Meetings, 2015, Carleton University), Sociology of Science (CSA Meetings, 2015, Carleton University), Sociology of Technology (CSA meetings, 2014, Brock University), Sociology of Culture (CSA meetings, 2014, Brock University)

\subsection*{2. Refereeing}

\subsubsection*{Journals}

\emph{Sociological Theory}, \emph{Canadian Journal of Sociology}

\subsubsection*{Promotion / Tenure Decisions}

NA

\subsubsection*{Grant Applications}

\subsubsection*{Architectural Juries}

NA

\subsubsection*{Visiting Critic Panels}

NA 

\subsection*{3. Editorial Duties}

NA

\subsection*{4. Consulting}

\end{document}